About the method
- `cluster_kmeans`: partitions data into `k` groups by minimizing within-cluster variance.

Didactic goal: establish the standard clustering line of experiment used throughout this family. Later examples should be read as changes in the clustering method, not as changes in the workflow.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages("daltoolbox")

library(daltoolbox)
```

Load data and separate predictors from the reference labels used only for interpretation.
```{r}
iris <- datasets::iris
x <- iris[, 1:4]
ref <- iris$Species
head(x)
```

Model configuration.
```{r}
model <- cluster_kmeans(k = 3)
model$eval_internal <- list(
  model$clu_utils$metric_silhouette,
  model$clu_utils$metric_davies_bouldin
)
model$eval_external <- list(
  model$clu_utils$metric_entropy,
  model$clu_utils$metric_purity
)
```

Fit the model and obtain cluster labels.
```{r}
set_example_seed()
model <- fit(model, x)
clu <- cluster(model, x)
table(clu)
```

Evaluate the partition.
```{r}
eval <- evaluate(model, clu, ref)
eval
```

What to observe
- The labels in `ref` are not used during fitting; they only help interpret the partition afterward.
- This is the reference clustering workflow used by the other examples in this family.

References
- MacQueen, J. (1967). Some Methods for Classification and Analysis of Multivariate Observations.
