About the method
- `cluster_pam`: Partitioning Around Medoids. Similar to k-means, but uses medoids instead of centroids.

Didactic goal: keep the same clustering line of experiment and change only the partitioning strategy.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages("daltoolbox")

library(daltoolbox)
```

Load data and separate predictors from the reference labels used only for interpretation.
```{r}
iris <- datasets::iris
x <- iris[, 1:4]
ref <- iris$Species
head(x)
```

Model configuration. The evaluation lists are customized here for a didactic reason: `silhouette` and `davies_bouldin` help compare the medoid partition through cohesion and separation, while `entropy` and `purity` make the external comparison with `iris$Species` easy to interpret. This keeps the discussion close to the k-means example so the reader can focus on the difference between centroids and medoids.
```{r}
model <- cluster_pam(k = 3)
model$eval_internal <- list(
  model$clu_utils$metric_silhouette,
  model$clu_utils$metric_davies_bouldin
)
model$eval_external <- list(
  model$clu_utils$metric_entropy,
  model$clu_utils$metric_purity
)
```

Fit the model and obtain cluster labels.
```{r}
set_example_seed()
model <- daltoolbox::fit(model, x)
clu <- daltoolbox::cluster(model, x)
table(clu)
```

Evaluate the partition.
```{r}
eval <- daltoolbox::evaluate(model, clu, ref)
eval
```

What to observe
- The workflow is unchanged from k-means.
- The method-specific difference is that medoids are actual observations, which can make the partition more robust to outliers.

References
- Kaufman, L., and Rousseeuw, P. J. (1990). Finding Groups in Data.
- Rousseeuw, P. J. (1987). Silhouettes: A graphical aid to the interpretation and validation of cluster analysis.
- Davies, D. L., and Bouldin, D. W. (1979). A cluster separation measure.
- Zhao, Y., and Karypis, G. (2001). Criterion functions for document clustering.
