About the method
- `cluster_dbscan`: density-based method. Identifies dense regions separated by sparse areas; detects noise and arbitrarily shaped clusters.

```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# Clustering - dbscan

# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Didactic goal: read this example as an unsupervised workflow. The emphasis is not on predicting a known label during training, but on understanding how the method groups the data and how preprocessing affects that grouping.

Load data (`iris`).
```{r}
# loading dataset
data(iris)
```

Configure DBSCAN; tune `minPts` (and `eps` if available) according to density.
```{r}
# clustering method configuration
model <- cluster_dbscan(minPts = 3)
model$eval_external <- list(
  model$clu_utils$metric_entropy,
  model$clu_utils$metric_purity
)
```

Fit and obtain cluster labels.
```{r}
# model fitting and labeling
set_example_seed()
model <- fit(model, iris[,1:4])
clu <- cluster(model, iris[,1:4])
table(clu)
```

External evaluation using `Species`, plus the internal count of noise points used by the default DBSCAN configuration.
```{r}
# evaluate model using internal and external metrics
eval <- evaluate(model, clu, iris$Species)
eval
```

References
- Ester, M., Kriegel, H.-P., Sander, J., Xu, X. (1996). A Density-Based Algorithm for Discovering Clusters in Large Spatial Databases with Noise.
