About the utility
- `clu_tune`: selects hyperparameters for a clustering method. In this example, it chooses `k` for `cluster_kmeans` over a range.

```{r}
# Clustering - Tune Kmeans

# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox)  
```

Didactic goal: read this example as an unsupervised workflow. The emphasis is not on predicting a known label during training, but on understanding how the method groups the data and how preprocessing affects that grouping.

Load data (`iris`).
```{r}
data(iris)
```

Fit the model with a search over k=1..10 and extract the best k.
```{r}
# model training with hyperparameter search
model <- clu_tune(cluster_kmeans(k = 0),  ranges = list(k = 1:10))
model <- fit(model, iris[,1:4])
model$k
```

Generate cluster labels with the best k.
```{r}
# run with best parameter
clu <- cluster(model, iris[,1:4])
table(clu)
```

External evaluation with `Species`.
```{r}
# external evaluation using ground truth labels
eval <- evaluate(model, clu, iris$Species)
eval
```

References
- Satopaa, V., Albrecht, J., Irwin, D., Raghavan, B. (2011). Finding a "Kneedle" in a Haystack: Detecting Knee Points in System Behavior.
