About the method
- `cluster_dbscan`: density-based clustering that identifies dense regions and can label sparse points as noise.

Didactic goal: keep the same clustering line of experiment and change only the grouping principle, from partitioning all cases to detecting dense neighborhoods.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages("daltoolbox")

library(daltoolbox)
```

Load data and separate predictors from the reference labels used only for interpretation.
```{r}
iris <- datasets::iris
x <- iris[, 1:4]
ref <- iris$Species
head(x)
```

Model configuration. The external evaluation list is customized here for a didactic reason: `entropy` summarizes how mixed each discovered region is relative to `iris$Species`, and `purity` offers a complementary, easier-to-read agreement score. The internal DBSCAN default remains method-specific, centered on the number of noise points rather than on a centroid-based criterion.
```{r}
model <- cluster_dbscan(minPts = 3)
model$eval_external <- list(
  model$clu_utils$metric_entropy,
  model$clu_utils$metric_purity
)
```

Fit the model and obtain cluster labels.
```{r}
set_example_seed()
model <- fit(model, x)
clu <- cluster(model, x)
table(clu)
```

Evaluate the partition.
```{r}
eval <- evaluate(model, clu, ref)
eval
```

What to observe
- The workflow is the same as in the partition-based methods.
- The method-specific difference is that DBSCAN may leave some cases as noise instead of forcing all observations into clusters.

References
- Ester, M., Kriegel, H.-P., Sander, J., and Xu, X. (1996). A Density-Based Algorithm for Discovering Clusters in Large Spatial Databases with Noise.
- Zhao, Y., and Karypis, G. (2001). Criterion functions for document clustering.
