About the method
- `cluster_cmeans`: fuzzy c-means clustering, which keeps membership degrees instead of only hard assignments.

Didactic goal: keep the same clustering line of experiment and change only the notion of assignment from hard clusters to soft memberships.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages("daltoolbox")

library(daltoolbox)
```

Load data and separate predictors from the reference labels used only for interpretation.
```{r}
iris <- datasets::iris
x <- iris[, 1:4]
ref <- iris$Species
head(x)
```

Model configuration.
```{r}
model <- cluster_cmeans(centers = 3, m = 2)
```

Fit the model and obtain cluster labels.
```{r}
set_example_seed()
model <- daltoolbox::fit(model, x)
clu <- daltoolbox::cluster(model, x)
table(clu)
```

Evaluate the partition.
```{r}
eval <- daltoolbox::evaluate(model, clu, ref)
eval
```

Inspect the membership matrix attached to the result.
```{r}
head(attr(clu, "membership"))
```

References
- Bezdek, J. C. (1981). Pattern Recognition with Fuzzy Objective Function Algorithms.
