About the method
- `cluster_gmm`: Gaussian mixture model clustering.

Didactic goal: keep the same clustering line of experiment and change only the clustering family to a probabilistic mixture model.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages(c("daltoolbox", "mclust"))

library(daltoolbox)
```

Load data and separate predictors from the reference labels used only for interpretation.
```{r}
iris <- datasets::iris
x <- iris[, 1:4]
ref <- iris$Species
head(x)
```

Model configuration.
```{r}
if (requireNamespace("mclust", quietly = TRUE)) {
  model <- cluster_gmm(G = 3)
}
```

Fit the model and obtain cluster labels.
```{r}
if (requireNamespace("mclust", quietly = TRUE)) {
  model <- fit(model, x)
  clu <- cluster(model, x)
  table(clu)
}
```

Evaluate the partition.
```{r}
if (requireNamespace("mclust", quietly = TRUE)) {
  eval <- evaluate(model, clu, ref)
  eval
}
```

References
- Fraley, C., and Raftery, A. E. (2002). Model-Based Clustering, Discriminant Analysis, and Density Estimation.
