About the method
- `cluster_hclust`: agglomerative hierarchical clustering.

Didactic goal: keep the same clustering line of experiment and add a hierarchy that can be inspected before or after cutting the tree into clusters.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages("daltoolbox")

library(daltoolbox)
```

Load data and separate predictors from the reference labels used only for interpretation.
```{r}
iris <- datasets::iris
x <- iris[, 1:4]
ref <- iris$Species
head(x)
```

Model configuration.
```{r}
model <- cluster_hclust(k = 3, method = "ward.D2")
```

Fit the model and obtain cluster labels.
```{r}
model <- fit(model, x)
clu <- cluster(model, x)
table(clu)
```

Evaluate the partition.
```{r}
eval <- evaluate(model, clu, ref)
eval
```

Inspect the hierarchy graphically.
```{r}
grf <- plot_dendrogram(model$hc, title = "Hierarchical clustering of iris")
plot(grf)
```

References
- Johnson, S. C. (1967). Hierarchical Clustering Schemes.
