About the method
- `cluster_louvain_graph`: graph community detection by modularity optimization.

Didactic goal: show the most important exception inside the clustering family. The workflow still follows the same DAL rhythm, but the input is now a graph instead of a feature matrix, and the interpretation is about communities rather than geometric groups.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages(c("daltoolbox", "igraph"))

library(daltoolbox)
library(igraph)
```

Create a graph for the example.
```{r}
set_example_seed()
g <- igraph::sample_gnp(n = 20, p = 0.15)
g
```

Model configuration.
```{r}
model <- cluster_louvain_graph()
```

Fit the model and obtain community labels.
```{r}
model <- fit(model, g)
clu <- cluster(model, g)
table(clu)
```

Inspect the modularity attached to the result.
```{r}
attr(clu, "modularity")
```

Optional graph view for interpretation.
```{r}
plot(
  g,
  vertex.color = as.factor(clu),
  vertex.label = NA,
  main = "Louvain communities"
)
```

What to observe
- The DAL workflow is still configure, fit, and cluster, but there is no feature matrix such as `iris[, 1:4]`.
- The returned groups are communities in a network, not partitions of points in Euclidean space.
- The attached modularity summarizes how strongly the discovered communities separate dense internal connections from sparse external ones.

Common mistakes
- Comparing this example too literally with centroid-based clustering, as if both were solving the same geometric problem.
- Expecting a reference label like `Species`; many graph problems are fully unsupervised and do not have an external class variable for evaluation.
- Reading modularity as an absolute guarantee of community truth rather than as a structural quality indicator for this partition on this graph.

References
- Blondel, V. D., Guillaume, J.-L., Lambiotte, R., and Lefebvre, E. (2008). Fast Unfolding of Communities in Large Networks.
