About the utility
- `clu_tune`: selects hyperparameters for a clustering method.
- In this example the tuned base model is `cluster_kmeans`.

Didactic goal: preserve the same clustering line of experiment and treat tuning as a change in configuration rather than as a different workflow.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages("daltoolbox")

library(daltoolbox)
```

Load data and separate predictors from the reference labels used only for interpretation.
```{r}
iris <- datasets::iris
x <- iris[, 1:4]
ref <- iris$Species
head(x)
```

Model configuration and tuning setup.
```{r}
base_model <- cluster_kmeans(k = 2)
base_model$metric <- base_model$clu_utils$metric_silhouette
base_model$selector <- base_model$clu_utils$selector_best
base_model$eval_internal <- list(base_model$clu_utils$metric_silhouette)
base_model$eval_external <- list(base_model$clu_utils$metric_entropy)

model <- clu_tune(base_model, ranges = list(k = 2:10))
```

Fit the tuned model and inspect the selected configuration.
```{r}
set_example_seed()
model <- fit(model, x)
model$k
```

Generate cluster labels with the selected configuration.
```{r}
clu <- cluster(model, x)
table(clu)
```

Evaluate the tuned partition.
```{r}
eval <- evaluate(model, clu, ref)
eval
```

What to observe
- The workflow is still configure, fit, cluster, and evaluate.
- Tuning changes how the clustering configuration is chosen, not how the experiment is read.

References
- Satopaa, V., Albrecht, J., Irwin, D., and Raghavan, B. (2011). Finding a "Kneedle" in a Haystack.
