About the method
- `cluster_kmeans`: partitions data into k groups by minimizing within-cluster variance. Sensitive to scale; normalization can improve results.

```{r}
# Clustering - Kmeans

# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox)  
```

Load sample data (`iris`).
```{r}
# loading dataset
data(iris)
```

Configure K-means with k=3 (one cluster per species in iris).
```{r}
# clustering method configuration
model <- cluster_kmeans(k=3)
```

Fit the model and obtain cluster labels.
```{r}
# model fitting and labeling
model <- fit(model, iris[,1:4])
clu <- cluster(model, iris[,1:4])
table(clu)
```

External evaluation using true labels (`Species`).
```{r}
# evaluate model using external metric
eval <- evaluate(model, clu, iris$Species)
eval
```


Effect of normalization: compare results after min-max.
```{r}
# Influence of normalization in clustering

iris_minmax <- transform(fit(minmax(), iris), iris)
model <- fit(model, iris_minmax[,1:4])
clu <- cluster(model, iris_minmax[,1:4])
table(clu)
```

Re-evaluation with normalized data.
```{r}
# evaluate model using external metric

eval <- evaluate(model, clu, iris_minmax$Species)
eval
```

