About the method
- `cla_boosting`: boosting classifier that builds a sequence of weak learners, each one focusing more on previously difficult cases.

Didactic goal: keep the line of experiment fixed and isolate the change in modeling idea. This helps the reader compare boosting with bagging and random forests without changing the data or evaluation structure.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages(c("daltoolbox", "adabag"))

library(daltoolbox)
```

Load data and inspect.
```{r}
iris <- datasets::iris
head(iris)
```

Target `Species` levels and reproducible train/test split.
```{r}
slevels <- levels(iris$Species)

set_example_seed()
sr <- train_test(sample_random(), iris)
iris_train <- sr$train
iris_test <- sr$test
```

Class distribution by split.
```{r}
tbl <- rbind(
  table(iris[, "Species"]),
  table(iris_train[, "Species"]),
  table(iris_test[, "Species"])
)
rownames(tbl) <- c("dataset", "training", "test")
tbl
```

Model configuration and fitting.
```{r}
if (requireNamespace("adabag", quietly = TRUE)) {
  model <- cla_boosting("Species", mfinal = 20)
  set_example_seed()
  model <- fit(model, iris_train)
}
```

Training evaluation.
```{r}
if (requireNamespace("adabag", quietly = TRUE)) {
  train_prediction <- predict(model, iris_train)
  train_eval <- evaluate(model, iris_train[, "Species"], train_prediction)
  train_eval$metrics
}
```

Test evaluation.
```{r}
if (requireNamespace("adabag", quietly = TRUE)) {
  test_prediction <- predict(model, iris_test)
  test_eval <- evaluate(model, iris_test[, "Species"], test_prediction)
  test_eval$metrics
}
```

What to observe
- Boosting changes the learner sequentially, not only by averaging independent resamples.
- The experiment body remains the same even though the ensemble logic differs from bagging and forests.

References
- Freund, Y., and Schapire, R. E. (1997). A Decision-Theoretic Generalization of On-Line Learning and an Application to Boosting.
