About the method
- `cla_glmnet`: L1-regularized logistic regression for binary classification.

Didactic goal: keep the same binary classification line of experiment used for `cla_glm` and change only the learner and its regularization choice.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages(c("daltoolbox", "glmnet"))

library(daltoolbox)
library(glmnet)
```

Load data, derive a binary target, and inspect.
```{r}
iris_bin <- datasets::iris
iris_bin$IsVersicolor <- factor(ifelse(
  iris_bin$Species == "versicolor",
  "versicolor",
  "not_versicolor"
))
head(iris_bin)
```

Target levels and reproducible stratified split.
```{r}
slevels <- levels(iris_bin$IsVersicolor)

set_example_seed()
sr <- train_test(sample_stratified("IsVersicolor"), iris_bin)
iris_train <- sr$train
iris_test <- sr$test
```

Class distribution by split.
```{r}
tbl <- rbind(
  table(iris_bin[, "IsVersicolor"]),
  table(iris_train[, "IsVersicolor"]),
  table(iris_test[, "IsVersicolor"])
)
rownames(tbl) <- c("dataset", "training", "test")
tbl
```

Model configuration and fitting.
```{r}
model <- cla_glmnet("IsVersicolor", lambda = "lambda.1se")
model <- fit(model, iris_train)
```

Training evaluation.
```{r}
train_prediction <- predict(model, iris_train)
train_eval <- evaluate(model, iris_train[, "IsVersicolor"], train_prediction)
train_eval$metrics
```

Test evaluation.
```{r}
test_prediction <- predict(model, iris_test)
test_eval <- evaluate(model, iris_test[, "IsVersicolor"], test_prediction)
test_eval$metrics
```

What to observe
- The binary experiment structure is unchanged from `cla_glm`.
- The key method-specific choice is how the penalized solution is selected through `lambda`.

References
- Friedman, J., Hastie, T., and Tibshirani, R. (2010). Regularization Paths for Generalized Linear Models via Coordinate Descent.
