About the method
- `cla_rpart`: CART-style classification tree using the `rpart` backend.

Didactic goal: keep the multiclass classification line of experiment fixed and change only the tree backend. This helps compare wrapper behavior without changing the semantic structure of the example.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages(c("daltoolbox", "rpart"))

library(daltoolbox)
library(rpart)
```

Load data and inspect.
```{r}
iris <- datasets::iris
head(iris)
```

Target `Species` levels and reproducible train/test split.
```{r}
slevels <- levels(iris$Species)

set_example_seed()
sr <- train_test(sample_random(), iris)
iris_train <- sr$train
iris_test <- sr$test
```

Class distribution by split.
```{r}
tbl <- rbind(
  table(iris[, "Species"]),
  table(iris_train[, "Species"]),
  table(iris_test[, "Species"])
)
rownames(tbl) <- c("dataset", "training", "test")
tbl
```

Model configuration and fitting.
```{r}
model <- cla_rpart("Species")
model <- fit(model, iris_train)
```

Training evaluation.
```{r}
train_prediction <- predict(model, iris_train)
train_eval <- evaluate(model, iris_train[, "Species"], train_prediction)
train_eval$metrics
```

Test evaluation.
```{r}
test_prediction <- predict(model, iris_test)
test_eval <- evaluate(model, iris_test[, "Species"], test_prediction)
test_eval$metrics
```

References
- Breiman, L., Friedman, J., Olshen, R., and Stone, C. (1984). Classification and Regression Trees.
