About the method
- `cla_xgboost`: gradient boosting classifier using the `xgboost` backend.

Didactic goal: keep the multiclass classification line of experiment fixed and show how a more configurable boosting engine still fits the same DAL workflow.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages(c("daltoolbox", "xgboost"))

library(daltoolbox)
```

Load data and inspect.
```{r}
iris <- datasets::iris
head(iris)
```

Target `Species` levels and reproducible train/test split.
```{r}
slevels <- levels(iris$Species)

set_example_seed()
sr <- train_test(sample_random(), iris)
iris_train <- sr$train
iris_test <- sr$test
```

Class distribution by split.
```{r}
tbl <- rbind(
  table(iris[, "Species"]),
  table(iris_train[, "Species"]),
  table(iris_test[, "Species"])
)
rownames(tbl) <- c("dataset", "training", "test")
tbl
```

Model configuration and fitting.
```{r}
if (requireNamespace("xgboost", quietly = TRUE)) {
  model <- cla_xgboost(
    "Species",
    params = list(max_depth = 2, eta = 0.2, nthread = 1),
    nrounds = 5
  )
  model <- fit(model, iris_train)
}
```

Training evaluation.
```{r}
if (requireNamespace("xgboost", quietly = TRUE)) {
  train_prediction <- predict(model, iris_train)
  train_eval <- evaluate(model, iris_train[, "Species"], train_prediction)
  train_eval$metrics
}
```

Test evaluation.
```{r}
if (requireNamespace("xgboost", quietly = TRUE)) {
  test_prediction <- predict(model, iris_test)
  test_eval <- evaluate(model, iris_test[, "Species"], test_prediction)
  test_eval$metrics
}
```

What to observe
- The experiment body is the same as in the other multiclass classification examples.
- The method-specific change is in the boosting engine and its configuration, not in the workflow.

References
- Chen, T., and Guestrin, C. (2016). XGBoost: A Scalable Tree Boosting System.
