About the utility
- `cla_tune`: performs hyperparameter search for a classifier over ranges defined in `ranges`.
- The example below tunes a `cla_svm` varying `epsilon`, `cost`, and `kernel`.

Environment setup.
```{r}
# Classification tuning 

# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Sample data and target levels.
```{r}
# Dataset for classification

iris <- datasets::iris
head(iris)

# extracting the levels for the dataset
slevels <- levels(iris$Species)
slevels
```

Train/test split
Random split for tuning validation.
```{r}
# preparing random sampling
set.seed(1)
sr <- sample_random()
sr <- train_test(sr, iris)
iris_train <- sr$train
iris_test <- sr$test

tbl <- rbind(table(iris[,"Species"]),
             table(iris_train[,"Species"]),
             table(iris_test[,"Species"]))
rownames(tbl) <- c("dataset", "training", "test")
head(tbl)
```

Hyperparameter grid and search training
```{r}
# Training with hyperparameter search
tune <- cla_tune(cla_svm("Species", slevels), 
  ranges = list(epsilon=seq(0,1,0.2), cost=seq(20,100,20), kernel = c("linear", "radial", "polynomial", "sigmoid")))

model <- fit(tune, iris_train)
```

Training evaluation with the best configuration
```{r}
# Training evaluation
train_prediction <- predict(model, iris_train)

iris_train_predictand <- adjust_class_label(iris_train[,"Species"])
train_eval <- evaluate(model, iris_train_predictand, train_prediction)
print(train_eval$metrics)
```

Test evaluation
```{r}
# Test evaluation
test_prediction <- predict(model, iris_test)

iris_test_predictand <- adjust_class_label(iris_test[,"Species"])

# Evaluating # setosa as primary class
test_eval <- evaluate(model, iris_test_predictand, test_prediction)
print(test_eval$metrics)
```

Example grids for other models
```{r}
# Grid options for other models
# knn
ranges <- list(k=1:20)

# mlp
ranges <- list(size=1:10, decay=seq(0, 1, 0.1))

# rf
ranges <- list(mtry=1:3, ntree=1:10)
```

References
- Kohavi, R. (1995). A Study of Cross-Validation and Bootstrap for Accuracy Estimation and Model Selection. IJCAI.
