About the method
- `cla_svm`: Support Vector Machine for classification, maximizing the margin between classes.
- Common hyperparameters: `cost` (penalty), `epsilon` (insensitive-margin width), and `kernel` (e.g., linear, radial, polynomial, sigmoid).

Environment setup: install and load the package.
```{r}
# Classification using Support Vector Machine

# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Load sample data (iris) and initial inspection.
```{r}
iris <- datasets::iris
head(iris)
```

Identify the target `Species` levels.
```{r}
# extracting the levels for the dataset
slevels <- levels(iris$Species)
slevels
```

# Building train and test samples via random sampling
Random train/test split.
```{r}
# Construindo amostras (treino e teste) por amostragem aleatória
set.seed(1)
sr <- sample_random()
sr <- train_test(sr, iris)
iris_train <- sr$train
iris_test <- sr$test
```

Check class distribution after the split.
```{r}

tbl <- rbind(table(iris[,"Species"]), 
             table(iris_train[,"Species"]), 
             table(iris_test[,"Species"]))
rownames(tbl) <- c("dataset", "training", "test")
head(tbl)
```

# Model training
Train SVM: tune `cost`, `epsilon`, and optionally `kernel`.
```{r}
# Treinamento do modelo
model <- cla_svm("Species", slevels, epsilon=0.0, cost=20.000) # kernel padrão; ajuste conforme necessário
model <- fit(model, iris_train)

```

# Training evaluation
Predict and compute metrics.
```{r}
# Verificando ajuste no treino
train_prediction <- predict(model, iris_train)

# Avaliação do modelo (treino)
iris_train_predictand <- adjust_class_label(iris_train[,"Species"])
train_eval <- evaluate(model, iris_train_predictand, train_prediction)
print(train_eval$metrics)
```

# Test evaluation
Predict and compute metrics.
```{r}
# Teste do modelo
test_prediction <- predict(model, iris_test)

iris_test_predictand <- adjust_class_label(iris_test[,"Species"])

# Avaliação no teste
 test_eval <- evaluate(model, iris_test_predictand, test_prediction)
print(test_eval$metrics)
```
