About the method
- `cla_rf`: Random Forest for classification. Ensemble of decision trees trained with randomness; robust and handles heterogeneous features well.
- Hyperparameters: `mtry` (variables per split), `ntree` (number of trees).

Environment setup.
```{r}
# Classification using  Random Forest

# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Load data and inspect.
```{r}
iris <- datasets::iris
head(iris)
```

Target `Species` levels.
```{r}
# extracting the levels for the dataset
slevels <- levels(iris$Species)
slevels
```

Building train and test samples via random sampling
Random train/test split.
```{r}
# Building train and test samples via random sampling
set.seed(1)
sr <- sample_random()
sr <- train_test(sr, iris)
iris_train <- sr$train
iris_test <- sr$test
```

Class distribution by split.
```{r}

tbl <- rbind(table(iris[,"Species"]), 
             table(iris_train[,"Species"]), 
             table(iris_test[,"Species"]))
rownames(tbl) <- c("dataset", "training", "test")
head(tbl)
```

Model training
Train Random Forest: tune `mtry` and `ntree`.
```{r}
# Model training
model <- cla_rf("Species", slevels, mtry=3, ntree=5) # mtry: variables per split; ntree: number of trees
model <- fit(model, iris_train)

```

Training evaluation
```{r}
# Checking fit on training data
train_prediction <- predict(model, iris_train)

# Model evaluation (training)
iris_train_predictand <- adjust_class_label(iris_train[,"Species"])
train_eval <- evaluate(model, iris_train_predictand, train_prediction)
print(train_eval$metrics)
```

Test evaluation
```{r}
# Model test
test_prediction <- predict(model, iris_test)

iris_test_predictand <- adjust_class_label(iris_test[,"Species"])

# Test evaluation
 test_eval <- evaluate(model, iris_test_predictand, test_prediction)
print(test_eval$metrics)
```

References
- Breiman, L. (2001). Random Forests. Machine Learning 45(1):5–32.
- Liaw, A. and Wiener, M. (2002). Classification and Regression by randomForest. R News.
