About the method
- `pat_apriori`: association-rule mining with semantic configuration stored in the miner object.

Didactic goal: establish the standard pattern-mining line of experiment used throughout this family: load data, configure the miner, `fit()`, `discover()`, `evaluate()`, and inspect the patterns.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages(c("daltoolbox", "arules"))

library(daltoolbox)
```

Load transactional data.
```{r}
data("AdultUCI", package = "arules")
trans <- suppressWarnings(methods::as(as.data.frame(AdultUCI), "transactions"))
summary(trans)
```

Model configuration.
```{r}
utils <- patutils()

pm <- pat_apriori(
  target = "rules",
  supp = 0.5,
  conf = 0.9,
  minlen = 2,
  maxlen = 4,
  rhs = c("income=small"),
  quality_filter = utils$quality_min(confidence = 0.95, lift = 1.05)
)
```

Fit and discover patterns.
```{r}
pm <- fit(pm, trans)
rules <- discover(pm, trans)
length(rules)
```

Evaluate the discovered patterns.
```{r}
eval <- evaluate(pm, rules)
eval$metrics
```

Inspect a few patterns.
```{r}
if (length(rules) == 0) {
  cat("No rules remained after the quality filter. Lower the thresholds if you want to inspect some candidates.\n")
} else {
  arules::inspect(rules[seq_len(min(6, length(rules)))])
}
```

What to observe
- The standard pattern-mining workflow is different from prediction, but it is still structured and reproducible.
- Later pattern examples will keep this same body and only change the pattern family and configuration.
