About the method
- `pat_apriori`: association-rule mining with semantic configuration stored in the miner object.

Didactic goal: establish the standard pattern-mining line of experiment used throughout this family with a directional rule example: fixed `rhs`, explicit confidence threshold, and quality filtering by lift.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages(c("daltoolbox", "arules"))

library(daltoolbox)
```

Load transactional data.
```{r}
data("AdultUCI", package = "arules")
trans <- suppressWarnings(methods::as(as.data.frame(AdultUCI), "transactions"))
summary(trans)
```

Model configuration.
```{r}
utils <- patutils()

pm <- pat_apriori(
  target = "rules",
  supp = 0.2,
  conf = 0.85,
  minlen = 2,
  maxlen = 3,
  rhs = c("native-country=United-States"),
  quality_filter = utils$quality_min(confidence = 0.9, lift = 1.03),
  control = list(verbose = FALSE)
)
```

Fit and discover patterns.
```{r}
pm <- fit(pm, trans)
rules <- suppressWarnings(discover(pm, trans))
length(rules)
```

Evaluate the discovered patterns.
```{r}
eval <- evaluate(pm, rules)
eval$metrics
```

Inspect a few patterns.
```{r}
ord <- order(arules::quality(rules)$lift, arules::quality(rules)$confidence, decreasing = TRUE)
arules::inspect(rules[head(ord, 6)])
```

What to observe
- The thresholds matter a lot. A didactic example should be configured to return some rules, not an empty result.
- Constraining the `rhs` is useful when you want rules that explain a specific consequent.
- `lift` works as a second filter on top of support and confidence, removing rules that are frequent but not especially informative.
- Later pattern examples will keep this same body and only change the pattern family and configuration.
