About the method
- `pat_apriori`: association-rule mining with semantic configuration in the object. Instead of sending raw engine lists, the user configures support, confidence, length, left-hand side, right-hand side, and optional quality filters as properties of the miner.

Didactic goal: read this example as a descriptive workflow. The value is not in predicting a target, but in understanding how the configuration of the search space changes the rules that survive.

```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# Pattern mining - apriori rules

# installation
# install.packages(c("daltoolbox", "arules"))

library(daltoolbox)
```

Load transactional data.
```{r}
data("AdultUCI", package = "arules")
trans <- suppressWarnings(methods::as(as.data.frame(AdultUCI), "transactions"))
summary(trans)
```

Configure the miner with semantic properties instead of raw engine arguments.
```{r}
utils <- patutils()

pm <- pat_apriori(
  target = "rules",
  supp = 0.5,
  conf = 0.9,
  minlen = 2,
  maxlen = 4,
  rhs = c("income=small"),
  quality_filter = utils$quality_min(confidence = 0.95, lift = 1.05)
)
```

Fit the miner and discover rules.
```{r}
pm <- fit(pm, trans)
rules <- discover(pm, trans)
length(rules)
```

Evaluate the discovered rules using the metrics configured by the object family.
```{r}
eval <- evaluate(pm, rules)
eval$metrics
```

Inspect a few rules.
```{r}
arules::inspect(rules[1:min(6, length(rules))])
```

What to observe
- `fit()` records the schema and compiles the engine configuration from semantic properties such as `supp`, `conf`, `lhs`, and `rhs`.
- `discover()` applies the mining engine and then optional quality filtering.
- `evaluate()` summarizes how many rules survived and how strong they are on average.

Common mistakes
- Treating `confidence` as if it were a predictive guarantee rather than a descriptive conditional frequency.
- Using a very restrictive `rhs` together with high `supp` and high `conf`, which may eliminate almost all rules.
- Interpreting large rule sets without any post-filtering.
