About the method
- `pat_eclat`: frequent itemset mining. Unlike association rules, the result is not directional; the goal is to identify groups of items that often appear together.

Didactic goal: read this example as a structural co-occurrence analysis. The important point is how support, maximum length, and item filters control the combinatorial search.

```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# Pattern mining - eclat itemsets

# installation
# install.packages(c("daltoolbox", "arules"))

library(daltoolbox)
```

Load the same transactional dataset used for rule mining.
```{r}
data("AdultUCI", package = "arules")
adult_df <- as.data.frame(AdultUCI)
head(adult_df)
```

Configure the miner with item filters and quality filtering.
```{r}
utils <- patutils()

pm <- pat_eclat(
  supp = 0.5,
  maxlen = 3,
  include = c("sex=Male", "income=small", "marital-status=Married-civ-spouse"),
  quality_filter = utils$quality_min(support = 0.55)
)
```

Fit and discover itemsets. Here the `fit()` step accepts a regular data frame and normalizes it internally to transactions.
```{r}
pm <- fit(pm, adult_df)
itemsets <- discover(pm, adult_df)
length(itemsets)
```

Evaluate the itemsets.
```{r}
eval <- evaluate(pm, itemsets)
eval$metrics
```

Inspect a few itemsets.
```{r}
arules::inspect(itemsets[1:min(6, length(itemsets))])
```

What to observe
- `include` and `exclude` act as DAL-level filters over the discovered itemsets.
- This makes the miner easier to adapt to an analytical question without exposing the user directly to engine-specific syntax.
- `evaluate()` now reports descriptive quality summaries for the mined patterns, not predictive error.

Common mistakes
- Confusing frequent itemsets with rules; itemsets do not imply direction.
- Setting `supp` too low on rich transactional data and generating an unmanageable number of combinations.
- Forgetting that coercing regular data to transactions may discretize non-categorical columns.
