About the method
- `pat_cspade`: sequential pattern mining. The central analytical question is no longer “which items co-occur?” but “which ordered event structures recur often enough to matter?”

Didactic goal: read this example as a sequence-discovery workflow. The most important lesson is that order-sensitive mining can still follow the same Experiment Line: configure the object, fit it, discover patterns, evaluate the result.

```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# Pattern mining - cspade sequences

# installation
# install.packages(c("daltoolbox", "arulesSequences"))

library(daltoolbox)
```

Load sequence transactions from the example dataset distributed with `arulesSequences`.
```{r}
x <- arulesSequences::read_baskets(
  con = system.file("misc", "zaki.txt", package = "arulesSequences"),
  info = c("sequenceID", "eventID", "SIZE")
)
x
```

Configure the miner with support and sequence-size restrictions.
```{r}
utils <- patutils()

pm <- pat_cspade(
  support = 0.4,
  maxlen = 3,
  quality_filter = utils$quality_min(support = 0.5),
  control = list(verbose = FALSE)
)
```

Fit and discover sequential patterns.
```{r}
pm <- fit(pm, x)
seqs <- discover(pm, x)
length(seqs)
```

Evaluate the resulting sequence set.
```{r}
eval <- evaluate(pm, seqs)
eval$metrics
```

Inspect a few patterns.
```{r}
head(as(seqs, "data.frame"))
```

What to observe
- `support` remains central, but now the patterns are ordered structures rather than unordered itemsets.
- `maxlen` controls sequence complexity and can be decisive for keeping the result interpretable.
- `evaluate()` summarizes the discovered sequence family without pretending that this is a supervised learning problem.

Common mistakes
- Reading sequential patterns as if they were ordinary association rules.
- Using very loose support thresholds and letting the number of sequences explode.
- Ignoring sequence length when interpreting the result.
