About the method
- `pat_eclat`: frequent itemset mining. The goal is to identify groups of items that often appear together.

Didactic goal: keep the same pattern-mining line of experiment and change only the discovered object type, from directional rules to unordered itemsets.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages(c("daltoolbox", "arules"))

library(daltoolbox)
```

Load transactional data.
```{r}
data("AdultUCI", package = "arules")
adult_df <- as.data.frame(AdultUCI)
head(adult_df)
```

Model configuration.
```{r}
utils <- patutils()

pm <- pat_eclat(
  supp = 0.5,
  maxlen = 3,
  include = c("sex=Male", "income=small", "marital-status=Married-civ-spouse"),
  quality_filter = utils$quality_min(support = 0.55)
)
```

Fit and discover patterns.
```{r}
pm <- fit(pm, adult_df)
itemsets <- discover(pm, adult_df)
length(itemsets)
```

Evaluate the discovered patterns.
```{r}
eval <- evaluate(pm, itemsets)
eval$metrics
```

Inspect a few patterns.
```{r}
if (length(itemsets) == 0) {
  cat("No itemsets remained after the quality filter. Lower the thresholds if you want to inspect some candidates.\n")
} else {
  arules::inspect(itemsets[seq_len(min(6, length(itemsets)))])
}
```

What to observe
- The workflow is unchanged from the rule-mining example.
- The main semantic change is that the result is now a set of itemsets, not a set of directional implications.
