About the method
- `pat_eclat`: frequent itemset mining. The goal is to identify groups of items that often appear together.

Didactic goal: show item-level filtering explicitly. Here the mining threshold defines the candidate pool, `include`/`exclude` restrict the item vocabulary, and the quality filter keeps only the strongest surviving itemsets.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages(c("daltoolbox", "arules"))

library(daltoolbox)
```

Load transactional data.
```{r}
data("AdultUCI", package = "arules")
trans <- suppressWarnings(methods::as(as.data.frame(AdultUCI), "transactions"))
summary(trans)
```

Model configuration.
```{r}
utils <- patutils()

pm <- pat_eclat(
  supp = 0.2,
  maxlen = 3,
  include = c("sex=Male", "income=small", "marital-status=Married-civ-spouse", "race=White"),
  exclude = c("income=small"),
  quality_filter = utils$quality_min(support = 0.4),
  control = list(verbose = FALSE)
)
```

Fit and discover patterns.
```{r}
pm <- fit(pm, trans)
itemsets <- discover(pm, trans)
length(itemsets)
```

Evaluate the discovered patterns.
```{r}
eval <- evaluate(pm, itemsets)
eval$metrics
```

Inspect a few patterns.
```{r}
ord <- order(arules::quality(itemsets)$support, decreasing = TRUE)
arules::inspect(itemsets[ord])
```

What to observe
- `include` and `exclude` act as semantic filters over which items may appear in the result.
- The quality filter is a second stage: it keeps only the itemsets that are still strong after the structural filtering.
- Itemsets are not directional rules. They capture co-occurrence, not implication.
