About the method
- `pat_cspade`: sequential pattern mining, where the analytical question is about recurring ordered event structures.

Didactic goal: keep the same pattern-mining line of experiment and change only the data type and pattern family so the reader can compare item co-occurrence with event order.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages(c("daltoolbox", "arulesSequences"))

library(daltoolbox)
```

Load sequence transactions.
```{r}
x <- arulesSequences::read_baskets(
  con = system.file("misc", "zaki.txt", package = "arulesSequences"),
  info = c("sequenceID", "eventID", "SIZE")
)
x
```

Model configuration.
```{r}
utils <- patutils()

pm <- pat_cspade(
  support = 0.4,
  maxlen = 3,
  quality_filter = utils$quality_min(support = 0.5),
  control = list(verbose = FALSE)
)
```

Fit and discover patterns.
```{r}
pm <- fit(pm, x)
seqs <- discover(pm, x)
length(seqs)
```

Evaluate the discovered patterns.
```{r}
eval <- evaluate(pm, seqs)
eval$metrics
```

Inspect a few patterns.
```{r}
head(as(seqs, "data.frame"))
```

What to observe
- The workflow is unchanged from the other pattern-mining examples.
- The main semantic change is that order now matters, so the discovered structures are sequences rather than itemsets or rules.
