About the method

- `pat_rule_filter_interest`: filters rules by classical interestingness measures such as `lift`, `Kulc`, and `IR`.
- `pat_rule_filter_dara`: filters rules by Divergent Association Ranking Analysis (DARA).
- `pat_rule_filter_none`: keeps all discovered rules and makes the no-filter option explicit.
- `pat_filter_rules`: applies an interesting-rule filter to a rule table or an `arules` rule object.

Didactic goal: separate pattern discovery from rule-interest filtering. `pat_apriori`, ECLAT, and other miners discover candidate patterns; rule filters keep the most interesting association rules according to either classical measures or DARA.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages(c("daltoolbox", "arules"))

library(daltoolbox)
```

Load categorical data.
```{r}
data("AdultUCI", package = "arules")

data <- as.data.frame(AdultUCI)
data <- data[, c(
  "workclass",
  "education",
  "marital-status",
  "occupation",
  "income"
)]
```

Mine target association rules and keep them in tabular form. This is the candidate rule set before interestingness filtering.
```{r}
rules <- pat_dara_rules(
  data,
  rhs = "income=small",
  supp = 0.05,
  conf = 0.6,
  minlen = 2,
  maxlen = 4,
  remove_redundant = FALSE
)

head(rules[, c("lhs", "rhs", "support", "confidence", "lift", "count")])
```

Keep all rules with the explicit no-filter option.
```{r}
none_rules <- pat_filter_rules(rules, pat_rule_filter_none())
nrow(none_rules)
```

Filter rules with classical interestingness measures. This keeps rules with high lift, acceptable Kulczynski, and low imbalance ratio.
```{r}
interest_filter <- pat_rule_filter_interest(
  lift_min = 1.2,
  kulc_min = 0.38,
  ir_max = 0.8
)

interest_rules <- pat_filter_rules(rules, interest_filter)
interest_rules[, c("lhs", "lift", "kulc", "ir")]
```

Filter rules with DARA. This scores each rule antecedent using divergence counters computed from the target subset.
```{r}
dara_filter <- pat_rule_filter_dara(
  data,
  rhs_attr = "income",
  rhs_value = "small",
  min_score = 1
)

dara_rules <- pat_filter_rules(rules, dara_filter)
dara_rules[, c("lhs", "dara_score")]
```

DARA can also be inspected as a ranking to explain why rules were retained.
```{r}
ranking <- attr(dara_rules, "dara_ranking")
ranking[["marital-status"]]
```

Use the DARA filter directly inside `pat_apriori`.
```{r}
pm <- pat_apriori(
  target = "rules",
  supp = 0.05,
  conf = 0.6,
  minlen = 2,
  maxlen = 4,
  rhs = "income=small",
  rule_filter = dara_filter,
  control = list(verbose = FALSE)
)

pm <- fit(pm, data)
filtered_rules <- discover(pm, data)
length(filtered_rules)
attr(filtered_rules, "dara_score")
```

What to observe

- Interestingness filters are post-processing components: the miner generates candidate rules, and the filter decides which rules remain.
- `pat_rule_filter_none()` is the explicit default when the user wants discovery without post-mining rule filtering.
- `lift`, `Kulc`, and `IR` evaluate a rule directly from support relationships.
- DARA evaluates whether antecedent values become more prominent in the rule set than in the target subset.
- DARA scores are attached to filtered rules through the `dara_score` column or attribute, and the explanatory ranking is available as `dara_ranking`.
