```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

# Pattern Mining

## Overview
Frequent pattern mining looks for regularities in transactional and sequential data. From frequent patterns, association rules can be derived with measures such as support, confidence, and lift.  
Slides: 1–5.

## How to read this guide
The flow is organized in four steps:
1. prepare transactional data;
2. mine itemsets and rules;
3. reduce redundancy and prioritize useful patterns;
4. move on to sequences and graphs.
At each step, compare pattern volume against interpretability.

## Setup

In this opening section, we load packages for mining, visualization, and structured variants (sequences/graphs).

```{r}
# Slides 1–3: context
# DAL ToolBox
# version 1.0.77

library(daltoolbox)

library(arules)
library(arulesViz)
library(arulesSequences)
library(igraph)
```

Before mining, inspect data size and a sample of the rows to understand cardinality and attribute types.

```{r}
# Slide 2–4: transactional example
data(AdultUCI)
myAdultUCI <- as.data.frame(AdultUCI)
dim(myAdultUCI)
head(myAdultUCI)
```

## Preprocessing and Concept Hierarchies
Discretization and the creation of aggregated levels help reduce cardinality and reveal patterns at different granularities.  
Slides: 5–9.

We start with minimal cleaning to prevent structural noise from distorting support and confidence.

```{r}
# Basic cleaning and attribute removal
na_obj <- na_removal()
myAdultUCI <- transform(na_obj, myAdultUCI)

myAdultUCI$fnlwgt <- NULL
myAdultUCI$"education-num" <- NULL
```

Next, we apply concept hierarchies and binning to improve interpretability without losing the global pattern.

```{r}
# Concept hierarchies and binning with DALToolbox transforms
hc_age <- hierarchy_cut(
  attribute = "age",
  breaks = c(15, 25, 45, 65, 100),
  labels = c("Young", "Middle-aged", "Senior", "Old"),
  new_attribute = "age_level"
)
myAdultUCI <- transform(hc_age, myAdultUCI)
myAdultUCI$age <- ordered(myAdultUCI$age_level, levels = c("Young", "Middle-aged", "Senior", "Old"))
myAdultUCI$age_level <- NULL

hc_hours <- hierarchy_cut(
  attribute = "hours-per-week",
  breaks = c(0, 25, 40, 60, 168),
  labels = c("Part-time", "Full-time", "Over-time", "Workaholic"),
  new_attribute = "hours_level"
)
myAdultUCI <- transform(hc_hours, myAdultUCI)
myAdultUCI$"hours-per-week" <- ordered(
  myAdultUCI$hours_level,
  levels = c("Part-time", "Full-time", "Over-time", "Workaholic")
)
myAdultUCI$hours_level <- NULL

gain_positive_median <- median(myAdultUCI$"capital-gain"[myAdultUCI$"capital-gain" > 0])
hc_gain <- hierarchy_cut(
  attribute = "capital-gain",
  breaks = c(-Inf, 0, gain_positive_median, Inf),
  labels = c("None", "Low", "High"),
  new_attribute = "capital_gain_level"
)
myAdultUCI <- transform(hc_gain, myAdultUCI)
myAdultUCI$"capital-gain" <- ordered(myAdultUCI$capital_gain_level, levels = c("None", "Low", "High"))
myAdultUCI$capital_gain_level <- NULL

loss_positive_median <- median(myAdultUCI$"capital-loss"[myAdultUCI$"capital-loss" > 0])
hc_loss <- hierarchy_cut(
  attribute = "capital-loss",
  breaks = c(-Inf, 0, loss_positive_median, Inf),
  labels = c("None", "Low", "High"),
  new_attribute = "capital_loss_level"
)
myAdultUCI <- transform(hc_loss, myAdultUCI)
myAdultUCI$"capital-loss" <- ordered(myAdultUCI$capital_loss_level, levels = c("None", "Low", "High"))
myAdultUCI$capital_loss_level <- NULL

head(myAdultUCI)
```

## Conversion to Transactions
Transactional data is the basis for Apriori, ECLAT, and association rules.  
Slides: 2–5.

```{r}
# Conversion to transactions
AdultTrans <- as(myAdultUCI, "transactions")
```

## Apriori
Apriori explores the anti-monotonic property of support to generate and prune candidates.  
Slides: 10–20.

Recommended reading: filter first by support/confidence and then prioritize by lift.

```{r}
# A Priori
pm_apriori <- pat_apriori(
  parameter = list(supp = 0.5, conf = 0.9, minlen = 2, maxlen = 10, target = "rules"),
  appearance = list(rhs = c("capital-gain=None"), default = "lhs"),
  control = NULL
)
pm_apriori <- fit(pm_apriori, AdultTrans)
rules <- discover(pm_apriori, AdultTrans)
inspect(rules)
```

Converting to `data.frame` makes rule ranking, filtering, and comparison easier.

```{r}
rules_a <- as(rules, "data.frame")
head(rules_a)
```

## ECLAT and Frequent Itemsets
ECLAT uses a vertical representation, which is efficient for support counting.  
Slides: 22–24.

This is a good place to compare with Apriori: ECLAT focuses on itemsets, while Apriori can already produce rules.

```{r}
# ECLAT (frequent itemsets)
pm_eclat <- pat_eclat(parameter = list(supp = 0.5, maxlen = 3))
pm_eclat <- fit(pm_eclat, AdultTrans)
itemsets_eclat <- discover(pm_eclat, AdultTrans)
inspect(head(sort(itemsets_eclat, by = "support")))
```

## Closed Patterns and Max-Patterns
Closed patterns preserve support; max-patterns reduce volume even further, but lose detail.  
Slides: 6–9.

These two sets help compress results without losing the main signal.

```{r}
# Closed patterns and max-patterns
closed_sets <- itemsets_eclat[is.closed(itemsets_eclat)]
max_sets <- itemsets_eclat[is.maximal(itemsets_eclat)]

inspect(head(sort(closed_sets, by = "support")))
inspect(head(sort(max_sets, by = "support")))
```

## Interestingness Measures
In addition to support and confidence, measures such as lift, leverage, and conviction help prioritize rules.  
Slides: 4–5, 21.

```{r}
# Rule analysis
imrules <- interestMeasure(rules, transactions = AdultTrans)
head(imrules)
```

In the next block, we sort by lift to highlight potentially more informative associations.

```{r}
imrules2 <- interestMeasure(rules, c("support", "confidence", "lift", "leverage", "conviction"), AdultTrans)
head(imrules2[order(imrules2[, "lift"], decreasing = TRUE), ])
```

## Redundancy and Interpretation
Reducing redundancy avoids repetitive or weakly informative rules.  
Slides: 21–24.

```{r}
# Removing redundant rules
nrules <- rules[!is.redundant(rules)]

arules::inspect(nrules)
```

## Supporting Transactions
Analyzing which transactions support the rules helps validate patterns.  
Slides: 4–5.

First we evaluate the coverage of one rule, then we extend it to multiple rules.

```{r}
# Showing the transactions that support the rules
st <- supportingTransactions(nrules[1], AdultTrans)
trans <- unique(st@data@i)
length(trans)
print(c(length(trans)/length(AdultTrans), nrules[1]@quality$support))
```

```{r}
# Supporting transactions for multiple rules
st <- supportingTransactions(nrules[1:2], AdultTrans)
trans <- unique(st@data@i)
length(trans)
print(c(length(trans)/length(AdultTrans), nrules[1:2]@quality$support))
```

## Rule Visualization
Visualizations help interpret the discovered patterns.  
Slides: 21.

Use the two plots in a complementary way: global view and relational view (`paracoord`).

```{r}
# Rule visualization
options(repr.plot.width=10, repr.plot.height=5)
plot(rules)
```

```{r}
options(repr.plot.width=10, repr.plot.height=5)
plot(rules, method="paracoord", control=list(reorder=TRUE))
```

## Rare and Negative Patterns
Rare patterns can be strategically important; negative patterns indicate inverse correlation (`lift < 1`).  
Slides: 39.

This step is useful for detecting exceptions and less frequent behaviors.

```{r}
# Rare and negative patterns
pm_apriori_rare <- pat_apriori(parameter = list(supp = 0.05, conf = 0.6, minlen = 2, maxlen = 3))
pm_apriori_rare <- fit(pm_apriori_rare, AdultTrans)
rare_rules <- discover(pm_apriori_rare, AdultTrans)
neg_rules <- subset(rare_rules, lift < 1)
length(neg_rules)
inspect(head(neg_rules))
```

## Multilevel and Multidimensional Associations
Rules can incorporate additional dimensions, such as demographic attributes, with suitable supports per level.  
Slides: 30–35.

Here we add a semantic dimension (`edu_level`) to extract more interpretable rules by profile.

```{r}
# Multilevel and multidimensional associations
adult_ml <- myAdultUCI
fg_edu <- feature_generation(
  edu_level = ifelse(
    education %in% c("Bachelors", "Masters", "Doctorate", "Prof-school"),
    "Higher",
    "Lower"
  )
)
adult_ml <- transform(fg_edu, adult_ml)
adult_ml$edu_level <- factor(adult_ml$edu_level)

AdultTransML <- as(adult_ml, "transactions")
income_labels <- paste0("income=", levels(adult_ml$income))

pm_apriori_md <- pat_apriori(
  parameter = list(supp = 0.2, conf = 0.6, minlen = 2, maxlen = 3),
  appearance = list(rhs = income_labels, default = "lhs")
)
pm_apriori_md <- fit(pm_apriori_md, AdultTransML)
rules_md <- discover(pm_apriori_md, AdultTransML)
inspect(rules_md)
```

## Sequence Mining
Sequential patterns extend itemsets to temporal order. SPADE is an efficient vertical approach.  
Slides: 46–62.

Key difference: in sequences, event order influences the discovered pattern.

```{r}
# Sequence mining
x <- read_baskets(con = system.file("misc", "zaki.txt", package = "arulesSequences"), info = c("sequenceID","eventID","SIZE"))
as(x, "data.frame")
```

With the data loaded, we run SPADE to discover frequent sequential patterns.

```{r}
pm_cspade <- pat_cspade(parameter = list(support = 0.4), control = list(verbose = TRUE))
pm_cspade <- fit(pm_cspade, x)
s1 <- discover(pm_cspade, x)
as(s1, "data.frame")
```

## Graph Pattern Mining (Example)
In graphs, frequent patterns are recurring subgraphs. Here we show subgraph counting as an illustration.  
Slides: 63–64.

We close with graphs to show that the concept of frequent patterns extends to relational structures.

```{r}
# Graph pattern mining (simple example)

g1 <- make_ring(4)
g2 <- make_full_graph(3)
g3 <- make_star(4, mode = "undirected")
tri <- make_full_graph(3)

count_subgraph_isomorphisms(tri, g1)
count_subgraph_isomorphisms(tri, g2)
count_subgraph_isomorphisms(tri, g3)
```

## References
- Han, J., Pei, J., & Tong, H. (2022). *Data Mining: Concepts and Techniques* (4th ed.). Morgan Kaufmann.
- Agrawal, R., & Srikant, R. (1994). Fast algorithms for mining association rules. *VLDB*.
- Zaki, M. (2001). SPADE: An efficient algorithm for mining frequent sequences. *Machine Learning*, 42(1), 31–60.
- Geng, L., & Hamilton, H. (2006). Interestingness measures for data mining: A survey. *ACM Computing Surveys*, 38(3).
- McGarry, K. (2005). A survey of interestingness measures for knowledge discovery. *Knowledge Engineering Review*, 20(1).
- Borgelt, C. (2005). An implementation of the FP-growth algorithm. *ACM SIGKDD Explorations*.
- Yan, X., & Han, J. (2002). gSpan: Graph-based substructure pattern mining. *ICDM*.
