About the transformation
- `sample_groups`: samples whole groups defined by a categorical attribute.

Didactic goal: show a sampling strategy where the unit of selection is the group, not the individual row. In sampling theory, this is known as cluster sampling (also called one-stage cluster sampling or sampling by groups). Here, "cluster" means a pre-existing group in the data, not a group inferred by k-means or another clustering algorithm. This matters when preserving within-group structure is more important than preserving the global distribution exactly.

```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages("daltoolbox")

library(daltoolbox)
```

```{r}
sc <- sample_groups("Species", n_groups = 2)
set_example_seed()
iris_sc <- transform(sc, datasets::iris)
table(iris_sc$Species)
```

What to observe
- Entire species groups are kept or removed together in this toy example.
- In practice, this kind of sampling is useful when rows belong to natural blocks that should not be split arbitrarily.
