About the transformation
- `imputation_tree`: iterative tree-based imputation for mixed datasets.

Didactic goal: contrast model-based imputation with simpler fill rules such as mean or median replacement. The method uses other attributes to predict missing values, which usually makes the imputation more context-aware.

```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages("daltoolbox")

library(daltoolbox)
```

Create a dataset with missing values in both numeric and categorical columns.
```{r}
iris_na <- datasets::iris
iris_na$Sepal.Length[c(2, 10, 25)] <- NA
iris_na$Petal.Width[c(5, 11)] <- NA
iris_na$Species[c(3, 15)] <- NA

summary(iris_na)
```

```{r}
imp <- imputation_tree(maxit = 3)
imp <- fit(imp, iris_na)
iris_imp <- transform(imp, iris_na)

summary(iris_imp$Sepal.Length)
table(iris_imp$Species, useNA = "ifany")
```

References
- Stekhoven, D. J., and Buhlmann, P. (2012). MissForest: non-parametric missing value imputation for mixed-type data.
