About the transformation
- `imputation_tree`: tree-based predictive imputation for one target column at a time.

Didactic goal: contrast model-based imputation with simpler fill rules such as mean or median replacement. The method uses other attributes to predict missing values in one target column, which keeps the API simple and makes the modeling role explicit.

```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages("daltoolbox")

library(daltoolbox)
```

Create a dataset with missing values in one target column.
```{r}
iris_na <- datasets::iris
iris_na$Sepal.Length[c(2, 10, 25)] <- NA

summary(iris_na)
```

```{r}
imp <- imputation_tree("Sepal.Length")
imp <- fit(imp, iris_na)
iris_imp <- transform(imp, iris_na)

summary(iris_imp$Sepal.Length)
sum(is.na(iris_imp$Sepal.Length))
```

References
- Breiman, L., Friedman, J., Olshen, R., Stone, C. (1984). Classification and Regression Trees.
- van Buuren, S., and Groothuis-Oudshoorn, K. (2011). mice: Multivariate Imputation by Chained Equations in R.
