## Random Class Undersampling

Random undersampling reduces all classes to the minority count by sampling without replacement.

Didactic goal: show the fastest way to reduce class imbalance and highlight its tradeoff. Undersampling is simple and often effective, but it discards information from the majority class to achieve balance.

```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# installation
# install.packages("daltoolbox")

library(daltoolbox)
```

Create an imbalanced dataset so the class reduction effect is easy to inspect.
```{r}
iris_imb <- datasets::iris[c(1:50, 51:71, 101:111), ]
table(iris_imb$Species)
```

Apply undersampling and inspect the new class distribution.
```{r}
set_example_seed()
bal <- bal_subsampling("Species")
iris_bal <- transform(bal, iris_imb)
table(iris_bal$Species)
head(iris_bal)
```

What to observe
- The balanced result is obtained by removing majority-class rows, not by creating new minority rows.
- This makes undersampling computationally cheap, but potentially more lossy than oversampling.
- As with any balancing transformation, apply it to training data only.

References
- He, H., and Garcia, E. A. (2009). Learning from Imbalanced Data. IEEE Transactions on Knowledge and Data Engineering.
