---
title: An R Markdown document converted from "Rmd/transf/categorical_mapping.ipynb"
output: html_document
---

## Categorical mapping
A categorical attribute with $n$ distinct values is mapped into $n$ binary attributes. 

It is also possible to map into $n-1$ binary values, where the scenario where all binary attributes are equal to zero corresponds to the last categorical value not indicated in the attributes.  

```{r}
# DAL ToolBox
# version 1.1.727

source("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/jupyter.R")

#loading DAL
load_library("daltoolbox")
```

### dataset for example 

```{r}
iris <- datasets::iris
head(iris)
```

### creating categorical mapping

```{r}
cm <- categ_mapping("Species")
iris_cm <- transform(cm, iris)
print(head(iris_cm))
```

### creating categorical mapping
Can be made from a single column, but needs to be a data frame

```{r}
diris <- iris[,"Species", drop=FALSE]
head(diris)
```

```{r}
iris_cm <- transform(cm, diris)
print(head(iris_cm))
```

