About the transformation
- `dt_pca`: Principal Component Analysis (PCA) projects correlated variables onto orthogonal components ordered by explained variance. You can let the tool pick the number of components via an elbow heuristic or set it explicitly.

Method
- Learns principal components via an orthogonal transformation (SVD/eigendecomposition of the covariance matrix), applied to centered/scaled numeric predictors.
- By default, the number of components is chosen via minimum-curvature (elbow) on the cumulative explained variance curve; alternatively set `components` manually.

Environment setup.
```{r}
# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Load data and PCA idea.
```{r}
# Dataset for example
iris <- datasets::iris
head(iris)
```

PCA
PCA finds a projection capturing the largest possible variance in the data. Below, we fit PCA and transform the dataset.

```{r}
# creates and fits PCA using the target column as reference
mypca <- dt_pca("Species")
mypca <- fit(mypca, datasets::iris)
iris.pca <- transform(mypca, iris)
```

PCA properties

```{r}
print(head(iris.pca))
print(head(mypca$pca.transf))
```

Manually set the number of components and repeat the transformation.
```{r}
# Manual definition of the number of components
mypca <- dt_pca("Species", 3)
mypca <- fit(mypca, datasets::iris)
iris.pca <- transform(mypca, iris)
print(head(iris.pca))
print(head(mypca$pca.transf))
```

References
- Pearson, K. (1901). On lines and planes of closest fit to systems of points in space.
- Hotelling, H. (1933). Analysis of a complex of statistical variables into principal components.
