```{r}
# installation 
install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Sobre a técnica
- `smoothing_inter`: discretização/suavização por intervalos regulares (larguras iguais). Útil para resumir variáveis contínuas em faixas.

Dados de exemplo e ideia geral de discretização/suavização.
```{r}
# Discretization & smoothing
# Discretization is the process of transferring continuous functions, models, variables, and equations into discrete counterparts. 

# Smoothing is a technique that creates an approximating function that attempts to capture important patterns in the data while leaving out noise or other fine-scale structures/rapid phenomena.

# An important part of the discretization/smoothing is to set up bins for proceeding the approximation.

# general function to evaluate different smoothing technique

iris <- datasets::iris
head(iris)
```

Aplicando discretização por intervalos e inspecionando os bins.
```{r}
# smoothing using regular interval
obj <- smoothing_inter(n = 2)  
obj <- fit(obj, iris$Sepal.Length)
sl.bi <- transform(obj, iris$Sepal.Length)
print(table(sl.bi))
obj$interval
```

Avaliando entropia condicional entre bins e espécie.
```{r}
entro <- evaluate(obj, as.factor(names(sl.bi)), iris$Species)
print(entro$entropy)
```

Otimizando o número de bins (busca em 1:20) e aplicando novamente.
```{r}
# Optimizing the number of binnings

opt_obj <- smoothing_inter(n=1:20)
obj <- fit(opt_obj, iris$Sepal.Length)
obj$n
```

```{r}
obj <- fit(obj, iris$Sepal.Length)
sl.bi <- transform(obj, iris$Sepal.Length)
print(table(sl.bi))
```
