```{r}
# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

About the technique
- `smoothing_inter`: discretization/smoothing by regular intervals (equal widths). Useful to summarize continuous variables into ranges.

Sample data and general idea of discretization/smoothing.
```{r}
# Discretization and smoothing
# Discretization: transform continuous functions, models, variables, and equations into discrete versions. 

# Smoothing: create an approximating function to capture important patterns, reducing noise and high-frequency variation.

# Defining bin intervals is essential to enable the approximation/discretization.

# General function to evaluate different smoothing techniques

iris <- datasets::iris
head(iris)
```

Apply interval-based discretization and inspect bins.
```{r}
# smoothing using regular interval
obj <- smoothing_inter(n = 2)  
obj <- fit(obj, iris$Sepal.Length)
sl.bi <- transform(obj, iris$Sepal.Length)
print(table(sl.bi))
obj$interval
```

Evaluate conditional entropy between bins and species.
```{r}
entro <- evaluate(obj, as.factor(names(sl.bi)), iris$Species)
print(entro$entropy)
```

Optimize the number of bins (search 1:20) and apply again.
```{r}
# Optimizing the number of binnings

opt_obj <- smoothing_inter(n=1:20)
obj <- fit(opt_obj, iris$Sepal.Length)
obj$n
```

```{r}
obj <- fit(obj, iris$Sepal.Length)
sl.bi <- transform(obj, iris$Sepal.Length)
print(table(sl.bi))
```
