About the transformation
- `dt_pca`: Principal Component Analysis (PCA) to project data onto orthogonal components with highest variance. Allows defining the number of components.

Environment setup.
```{r}
# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Load data and PCA idea.
```{r}
# Dataset for example
iris <- datasets::iris
head(iris)
```

# PCA
PCA finds a projection capturing the largest possible variance in the data. Below, we fit PCA and transform the dataset.

```{r}
# cria e ajusta PCA usando a coluna alvo para referência
mypca <- dt_pca("Species")
mypca <- fit(mypca, datasets::iris)
iris.pca <- transform(mypca, iris)
```

# PCA properties

```{r}
print(head(iris.pca))
print(head(mypca$pca.transf))
```

Manually set the number of components and repeat the transformation.
```{r}
# Definição manual do número de componentes
mypca <- dt_pca("Species", 3)
mypca <- fit(mypca, datasets::iris)
iris.pca <- transform(mypca, iris)
print(head(iris.pca))
print(head(mypca$pca.transf))
```
