About the technique
- `smoothing_freq`: discretization/smoothing by frequency (quantiles), producing bins with similar counts.

```{r}
# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Sample data and general idea.
```{r}
# Discretization and smoothing
# Discretization: transform continuous functions, models, variables, and equations into discrete versions. 

# Smoothing: create an approximating function to capture important patterns, reducing noise and high-frequency variation.

# Defining bin intervals is essential to enable the approximation/discretization.

# General function to evaluate different smoothing techniques

iris <- datasets::iris
head(iris)
```

Apply frequency-based discretization and inspect intervals.
```{r}
# smoothing using regular frequency

obj <- smoothing_freq(n = 2)  
obj <- fit(obj, iris$Sepal.Length)
sl.bi <- transform(obj, iris$Sepal.Length)
print(table(sl.bi))
obj$interval
```

Evaluate conditional entropy.
```{r}
entro <- evaluate(obj, as.factor(names(sl.bi)), iris$Species)
print(entro$entropy)
```

Optimize the number of bins and apply again.
```{r}
# Optimizing the number of binnings

opt_obj <- smoothing_freq(n=1:20)
obj <- fit(opt_obj, iris$Sepal.Length)
obj$n
```

```{r}
obj <- fit(obj, iris$Sepal.Length)
sl.bi <- transform(obj, iris$Sepal.Length)
print(table(sl.bi))
```

References
- Han, J., Kamber, M., Pei, J. (2011). Data Mining: Concepts and Techniques. (Discretization)

