About the technique
- `smoothing_cluster`: discretization/smoothing by defining bins via clustering instead of fixed intervals.

# Discretization and smoothing
Discretization transforms continuous functions, models, variables, and equations into discrete counterparts.

Smoothing creates an approximating function to capture important patterns while reducing noise or high-frequency variation.

Defining bin intervals is an important step to enable the approximation.

```{r}
# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```


# General function to evaluate different smoothing techniques

Sample data (`iris`) to illustrate clustering-based discretization/smoothing.
```{r}
iris <- datasets::iris
head(iris)
```

Apply clustering-based smoothing and inspect bins.
```{r}
# smoothing using clustering
obj <- smoothing_cluster(n = 2)  
obj <- fit(obj, iris$Sepal.Length)
sl.bi <- transform(obj, iris$Sepal.Length)
print(table(sl.bi))
obj$interval
```

Evaluate conditional entropy between bins and species.
```{r}
entro <- evaluate(obj, as.factor(names(sl.bi)), iris$Species)
print(entro$entropy)
```

# Optimizing the number of binnings

Optimize the number of bins (search 1:20) and refit.
```{r}
opt_obj <- smoothing_cluster(n=1:20)
obj <- fit(opt_obj, iris$Sepal.Length)
obj$n
```

```{r}
obj <- fit(obj, iris$Sepal.Length)
sl.bi <- transform(obj, iris$Sepal.Length)
print(table(sl.bi))
```

References
- MacQueen, J. (1967). Some Methods for Classification and Analysis of Multivariate Observations.
