About the transformation
- `zscore`: standardizes numeric attributes to zero mean and unit variance. You can also rescale to a target mean (`nmean`) and standard deviation (`nsd`).

Method
- For each numeric column j: `(x - mean_j) / sd_j` and optionally `* nsd + nmean`.
- Constant columns (zero variance) map to `nmean`.

When to use
- Useful to equalize scale across features and as input to scale-sensitive models (e.g., k-NN, SVM with RBF kernel, PCA).

Environment setup.
```{r}
# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Context and sample data (iris).
```{r}
# Normalization

# Normalization is a technique used to equal strength among variables. 

# It is also important to apply it as an input for some machine learning methods. 

# Example

iris <- datasets::iris  
summary(iris)
```

Apply standard Z-Score (mean = 0, sd = 1) and inverse-transform.
```{r}
# Z-Score

# Adjust values to 0 (mean), 1 (variance).

norm <- zscore()
norm <- fit(norm, iris)
ndata <- transform(norm, iris)
summary(ndata)

ddata <- inverse_transform(norm, ndata)
summary(ddata)
```

Standardization to custom target mean and standard deviation.
```{r}
norm <- zscore(nmean=0.5, nsd=0.5/2.698)
norm <- fit(norm, iris)
ndata <- transform(norm, iris)
summary(ndata)
```

Inverse transform for checking.
```{r}
ddata <- inverse_transform(norm, ndata)
summary(ddata)
```

References
- Han, J., Kamber, M., Pei, J. (2011). Data Mining: Concepts and Techniques. (Standardization)
