About the transformation
- `minmax`: linearly rescales numeric attributes to a target range (default [0, 1]). Useful for scale-sensitive algorithms and models that expect bounded inputs.

Method
- For each numeric column j: `(x - min_j) / (max_j - min_j)` to map to [0, 1].
- Constant columns (where `max_j == min_j`) map to 0 to avoid division by zero.

When to use
- Recommended for distance-based methods (e.g., k-NN), gradient methods sensitive to feature scales, or when features have different units.

Environment setup.
```{r}
# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Context and sample data (iris) to illustrate normalization.
```{r}
# Normalization

# Normalization is a technique used to equal strength among variables. 

# It is also important to apply it as an input for some machine learning methods. 

# Example

iris <- datasets::iris  
summary(iris)
```

Apply Min-Max and inspect the resulting scale.
```{r}
# Min-Max 
# Adjust numeric values to 0 (minimum value) - 1 (maximum value).

norm <- minmax()
norm <- fit(norm, iris)
ndata <- transform(norm, iris)
summary(ndata)
```

Inverse transform (denormalize) to verify integrity.
```{r}
ddata <- inverse_transform(norm, ndata)
summary(ddata)
```

References
- Han, J., Kamber, M., Pei, J. (2011). Data Mining: Concepts and Techniques. (Normalization section)
