About sampling
- `sample_random`: splits train/test sets and creates folds via random draws, preserving only expected proportions on average.

Environment setup.
```{r}
# Sampling dataset

# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Load dataset and view class distribution.
```{r}
iris <- datasets::iris
head(iris)
table(iris$Species)
```

Split into train/test with random sampling (distributions may vary by draw).
```{r}
# Split into train and test

# using random sampling
tt <- train_test(sample_random(), iris)

# training distribution
print(table(tt$train$Species))

# test distribution
print(table(tt$test$Species))
```

Create random k-folds and check distribution per fold.
```{r}
# Split the dataset into folds

# preparing the dataset into four folds
sample <- sample_random()
folds <- k_fold(sample, iris, 4)

# folds distribution
tbl <- NULL
for (f in folds) {
tbl <- rbind(tbl, table(f$Species))
}
print(tbl)
```

References
- Kohavi, R. (1995). A Study of Cross-Validation and Bootstrap for Accuracy Estimation and Model Selection. IJCAI.
