About sampling
- `sample_stratified`: splits train/test and folds preserving the target variable proportion (stratification) per category.

Environment setup.
```{r}
# Stratified sampling dataset

# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Load dataset and view class distribution.
```{r}
iris <- datasets::iris
head(iris)
table(iris$Species)
```

Stratified train/test split preserving `Species` proportions.
```{r}
# Split into train and test

# using stratified sampling
tt <- train_test(sample_stratified("Species"), iris)

# training distribution
print(table(tt$train$Species))

# test distribution
print(table(tt$test$Species))
```

Create stratified folds and check distribution.
```{r}
# Split the dataset into folds

# using stratified sampling
# preparing the dataset into four folds
sample <- sample_stratified("Species")
folds <- k_fold(sample, iris, 4)

# folds distribution
tbl <- NULL
for (f in folds) {
tbl <- rbind(tbl, table(f$Species))
}
print(tbl)
```

References
- Kohavi, R. (1995). A Study of Cross-Validation and Bootstrap for Accuracy Estimation and Model Selection. IJCAI. (advocates stratified sampling)
