## LSTM Autoencoder transformation (encode-decode)

Considering a dataset with $p$ numerical attributes. 

The goal of the autoencoder is to reduce the dimension of $p$ to $k$, such that these $k$ attributes are enough to recompose the original $p$ attributes. However from the $k$ dimensionals the data is returned back to $p$ dimensions. The higher the quality of autoencoder the similiar is the output from the input. 

```{r}
# DAL ToolBox
# version 1.1.737



#loading DAL
library(daltoolbox)
library(ggplot2)
```

### dataset for example 

```{r}
data(sin_data)

sw_size <- 5
ts <- ts_data(sin_data$y, sw_size)

ts_head(ts)
```

### applying data normalization

```{r}
preproc <- ts_norm_gminmax()
preproc <- fit(preproc, ts)
ts <- transform(preproc, ts)

ts_head(ts)
```

### spliting into training and test

```{r}
samp <- ts_sample(ts, test_size = 10)
train <- as.data.frame(samp$train)
test <- as.data.frame(samp$test)
```

### creating autoencoder
Reduce from 5 to 3 dimensions

```{r}
auto <- autoenc_lstm_ed(5, 3, num_epochs=1500)

auto <- fit(auto, train)
```

### learning curves

```{r}
fit_loss <- data.frame(x=1:length(auto$train_loss), train_loss=auto$train_loss,val_loss=auto$val_loss)

grf <- plot_series(fit_loss, colors=c('Blue','Orange'))
plot(grf)
```

### testing autoencoder
presenting the original test set and display encoding

```{r}
print(head(test))
result <- transform(auto, test)
print(head(result))
```

```{r}
result <- as.data.frame(result)
names(result) <- names(test)
r2 <- c()
mape <- c()
for (col in names(test)){
r2_col <- cor(test[col], result[col])^2
r2 <- append(r2, r2_col)
mape_col <- mean((abs((result[col] - test[col]))/test[col])[[col]])
mape <- append(mape, mape_col)
print(paste(col, 'R2 test:', r2_col, 'MAPE:', mape_col))
}
print(paste('Means R2 test:', mean(r2), 'MAPE:', mean(mape)))
```

