## Variational Autoencoder transformation (encode)

Considering a dataset with $p$ numerical attributes. 

The goal of the autoencoder is to reduce the dimension of $p$ to $k$, such that these $k$ attributes are enough to recompose the original $p$ attributes. 

```{r}
# DAL ToolBox
# version 1.1.737



#loading DAL
library(daltoolbox)
library(ggplot2)
```

### dataset for example 

```{r}
data(sin_data)

sw_size <- 5
ts <- ts_data(sin_data$y, sw_size)

ts_head(ts)
```

### applying data normalization

```{r}
preproc <- ts_norm_gminmax()
preproc <- fit(preproc, ts)
ts <- transform(preproc, ts)

ts_head(ts)
```

### spliting into training and test

```{r}
samp <- ts_sample(ts, test_size = 10)
train <- as.data.frame(samp$train)
test <- as.data.frame(samp$test)
```

### creating autoencoder
Reduce from 5 to 3 dimensions

```{r}
auto <- varae_encode(5, 3, num_epochs=350)

auto <- fit(auto, train)
```

### learning curves

```{r}
train_loss <- unlist(auto$model$train_loss)
val_loss <- unlist(auto$model$val_loss)

fit_loss <- as.data.frame(cbind(train_loss, val_loss))
fit_loss['epoch'] <- 1:nrow(fit_loss)

ggplot(fit_loss, aes(x=epoch)) +
geom_line(aes(y=train_loss, colour='Train Loss')) +
geom_line(aes(y=val_loss, colour='Val Loss')) +
scale_color_manual(values=c('Blue','Orange')) +
theme_classic()
```

### testing autoencoder
presenting the original test set and display encoding

```{r}
print(head(test))
result <- transform(auto, test)
print(head(result))
```

