About the method
- `reg_dtree`: decision tree for regression. Partitions feature space and predicts numeric values by leaf means.

Didactic goal: establish the standard regression line of experiment used throughout this family of examples.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages("daltoolbox")

library(daltoolbox)
```

Load data and inspect.
```{r}
data(Boston)
head(Boston)
```

Target `medv` and reproducible train/test split.
```{r}
set_example_seed()
sr <- train_test(sample_random(), Boston)
boston_train <- sr$train
boston_test <- sr$test
```

Model configuration and fitting.
```{r}
model <- reg_dtree("medv")
set_example_seed()
model <- fit(model, boston_train)
```

Training evaluation.
```{r}
train_prediction <- predict(model, boston_train)
train_eval <- evaluate(model, boston_train[, "medv"], train_prediction)
train_eval$metrics
```

Test evaluation.
```{r}
test_prediction <- predict(model, boston_test)
test_eval <- evaluate(model, boston_test[, "medv"], test_prediction)
test_eval$metrics
```

What to observe
- The regression workflow already has the same structural rhythm as classification.
- What changes is the target type and the interpretation of the evaluation metrics.

References
- Breiman, L., Friedman, J., Olshen, R., and Stone, C. (1984). Classification and Regression Trees.
