About the method
- `reg_lm`: ordinary linear regression model.

Didactic goal: preserve the same regression line of experiment and use a linear model as a reference point before comparing nonlinear or ensemble regressors.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages("daltoolbox")

library(daltoolbox)
```

Load data and inspect.
```{r}
data(Boston)
head(Boston)
```

Target `medv` and reproducible train/test split.
```{r}
set_example_seed()
sr <- train_test(sample_random(), Boston)
boston_train <- sr$train
boston_test <- sr$test
```

Model configuration and fitting.
```{r}
model <- reg_lm(attribute = "medv")
model <- fit(model, boston_train)
```

Training evaluation.
```{r}
train_prediction <- predict(model, boston_train)
train_eval <- evaluate(model, boston_train[, "medv"], train_prediction)
train_eval$metrics
```

Test evaluation.
```{r}
test_prediction <- predict(model, boston_test)
test_eval <- evaluate(model, boston_test[, "medv"], test_prediction)
test_eval$metrics
```

What to observe
- The regression workflow is the same as in the other examples.
- The method-specific difference is the linear relationship assumed between predictors and target.

References
- Montgomery, D. C., Peck, E. A., and Vining, G. G. (2021). Introduction to Linear Regression Analysis.
