About the method
- `reg_svm`: Support Vector Regression.
- Main parameters: `epsilon`, `cost`, and `kernel`.

Didactic goal: keep the same regression line of experiment and change only the learner to a margin-based regressor.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages("daltoolbox")

library(daltoolbox)
```

Load data and inspect.
```{r}
data(Boston)
head(Boston)
```

Target `medv` and reproducible train/test split.
```{r}
set_example_seed()
sr <- train_test(sample_random(), Boston)
boston_train <- sr$train
boston_test <- sr$test
```

Model configuration and fitting.
```{r}
model <- reg_svm("medv", epsilon = 0.2, cost = 40.0)
set_example_seed()
model <- fit(model, boston_train)
```

Training evaluation.
```{r}
train_prediction <- predict(model, boston_train)
train_eval <- evaluate(model, boston_train[, "medv"], train_prediction)
train_eval$metrics
```

Test evaluation.
```{r}
test_prediction <- predict(model, boston_test)
test_eval <- evaluate(model, boston_test[, "medv"], test_prediction)
test_eval$metrics
```

References
- Drucker, H., Burges, C., Kaufman, L., Smola, A., and Vapnik, V. (1997). Support Vector Regression Machines.
