About the utility
- `reg_tune`: hyperparameter search for regression models over ranges defined in `ranges`.
- In this example the tuned base learner is `reg_svm`.

Didactic goal: preserve the same regression line of experiment and treat tuning as a change in model configuration rather than as a separate workflow.

Environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages("daltoolbox")

library(daltoolbox)
```

Load data and inspect.
```{r}
data(Boston)
head(Boston)
```

Target `medv` and reproducible train/test split.
```{r}
set_example_seed()
sr <- train_test(sample_random(), Boston)
boston_train <- sr$train
boston_test <- sr$test
```

Model configuration and fitting.
```{r}
tune <- reg_tune(
  reg_svm("medv"),
  ranges = list(
    epsilon = seq(0, 1, 0.2),
    cost = seq(20, 100, 20),
    kernel = c("radial")
  )
)

set_example_seed()
model <- fit(tune, boston_train)
```

Training evaluation.
```{r}
train_prediction <- predict(model, boston_train)
train_eval <- evaluate(model, boston_train[, "medv"], train_prediction)
train_eval$metrics
```

Test evaluation.
```{r}
test_prediction <- predict(model, boston_test)
test_eval <- evaluate(model, boston_test[, "medv"], test_prediction)
test_eval$metrics
```

What to observe
- The workflow is still split, fit, predict, and evaluate.
- Tuning changes how the regressor is chosen, not how the line of experiment is structured.

References
- Kohavi, R. (1995). A Study of Cross-Validation and Bootstrap for Accuracy Estimation and Model Selection.
