About the method
- `reg_dtree`: decision tree for regression. Partitions feature space and estimates values by leaf means; interpretable and can model nonlinearities.

Environment setup.
```{r}
# Regression Decision Tree

# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Load Boston dataset (MASS) and inspect types.
```{r}
# Dataset for regression analysis

library(MASS)
data(Boston)
print(t(sapply(Boston, class)))
head(Boston)
```

Optional conversion to matrix for performance in some methods.
```{r}
# for performance, you can convert to matrix
Boston <- as.matrix(Boston)
```

Random train/test split.
```{r}
# preparing dataset for random sampling
set.seed(1)
sr <- sample_random()
sr <- train_test(sr, Boston)
boston_train <- sr$train
boston_test <- sr$test
```

Train regression tree model to predict `medv`.
```{r}
# Training

model <- reg_dtree("medv")
model <- fit(model, boston_train)
```

Training evaluation (regression metrics, e.g., RMSE, MAE).
```{r}
# Model adjustment

train_prediction <- predict(model, boston_train)
boston_train_predictand <- boston_train[,"medv"]
train_eval <- evaluate(model, boston_train_predictand, train_prediction)
print(train_eval$metrics)
```

Test evaluation.
```{r}
# Test

test_prediction <- predict(model, boston_test)
boston_test_predictand <- boston_test[,"medv"]
test_eval <- evaluate(model, boston_test_predictand, test_prediction)
print(test_eval$metrics)
```

References
- Breiman, L., Friedman, J., Olshen, R., and Stone, C. (1984). Classification and Regression Trees. Wadsworth.
