About the utility
- `reg_tune`: hyperparameter search for regression models over ranges in `ranges`.
- Example: tuning `reg_svm` varying `epsilon`, `cost`, and `kernel`.

Environment setup.
```{r}
# Tuning de Regressão 

# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Load dataset and inspect.
```{r}
# Conjunto de dados para análise de regressão

library(MASS)
data(Boston)
print(t(sapply(Boston, class)))
head(Boston)
```

Optional conversion to matrix.
```{r}
# por desempenho, você pode converter para matriz
Boston <- as.matrix(Boston)
```

Train/test split for tuning validation.
```{r}
# preparing dataset for random sampling
set.seed(1)
sr <- sample_random()
sr <- train_test(sr, Boston)
boston_train <- sr$train
boston_test <- sr$test
```

Hyperparameter grid configuration and search training.
```{r}
# Training

tune <- reg_tune(reg_svm("medv"), 
          ranges = list(seq(0,1,0.2), cost=seq(20,100,20), kernel = c("radial")))
model <- fit(tune, boston_train)
```

Training evaluation with the best hyperparameters.
```{r}
# Model adjustment

train_prediction <- predict(model, boston_train)
boston_train_predictand <- boston_train[,"medv"]
train_eval <- evaluate(model, boston_train_predictand, train_prediction)
print(train_eval$metrics)
```

Test evaluation.
```{r}
# Test

test_prediction <- predict(model, boston_test)
boston_test_predictand <- boston_test[,"medv"]
test_eval <- evaluate(model, boston_test_predictand, test_prediction)
print(test_eval$metrics)
```

Example grids for other models.
```{r}
# Options for other models

# svm
ranges <- list(seq(0,1,0.2), cost=seq(20,100,20), kernel = c("linear", "radial", "polynomial", "sigmoid"))

# knn
ranges <- list(k=1:20)

# mlp
ranges <- list(size=1:10, decay=seq(0, 1, 0.1))

# rf
ranges <- list(mtry=1:10, ntree=1:10)
```
