About the method
- `reg_svm`: Support Vector Regression (SVR). Models a function with an error-insensitive margin up to `epsilon` and penalizes violations via `cost`.
- Hyperparameters: `epsilon`, `cost`, and `kernel` (if applicable).

Environment setup.
```{r}
# Regression SVM

# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

Load Boston dataset (MASS) and inspect types.
```{r}
# Conjunto de dados para análise de regressão

library(MASS)
data(Boston)
print(t(sapply(Boston, class)))
head(Boston)
```

Optional conversion to matrix.
```{r}
# por desempenho, você pode converter para matriz
Boston <- as.matrix(Boston)
```

Random and reproducible train/test split.
```{r}
# preparing dataset for random sampling

set.seed(1)
sr <- sample_random()
sr <- train_test(sr, Boston)
boston_train <- sr$train
boston_test <- sr$test
```

Train SVR: set `epsilon` and `cost` (default kernel if not defined).
```{r}
# Training

model <- reg_svm("medv", epsilon=0.2,cost=40.000)
model <- fit(model, boston_train)
```

Training evaluation.
```{r}
# Model adjustment

train_prediction <- predict(model, boston_train)
boston_train_predictand <- boston_train[,"medv"]
train_eval <- evaluate(model, boston_train_predictand, train_prediction)
print(train_eval$metrics)
```

Test evaluation.
```{r}
# Test

test_prediction <- predict(model, boston_test)
boston_test_predictand <- boston_test[,"medv"]
test_eval <- evaluate(model, boston_test_predictand, test_prediction)
print(test_eval$metrics)
```
