# Regression Random Forest

About the method
- `reg_rf`: Random Forest for regression. Averages many decision trees trained with randomness; tends to reduce variance.
- Hyperparameters: `mtry` (variables per split), `ntree` (number of trees).

```{r}
# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

# Dataset for regression analysis
Load Boston dataset and inspect types/values.

```{r}
library(MASS)
data(Boston)
print(t(sapply(Boston, class)))
head(Boston)
```

# Optional conversion to matrix (may improve performance in some cases).
```{r}
# for performance, you can convert to matrix
Boston <- as.matrix(Boston)
```

# Train/test split
Random and reproducible train/test split.

```{r}
# preparing random sampling
set.seed(1)
sr <- sample_random()
sr <- train_test(sr, Boston)
boston_train <- sr$train
boston_test <- sr$test
```

# Training
Train Random Forest to predict `medv`.

```{r}
model <- reg_rf("medv", mtry=7, ntree=30) # mtry: variables per split; ntree: number of trees
model <- fit(model, boston_train)
```

# Model adjustment
Training evaluation (regression metrics such as RMSE/MAE).

```{r}
train_prediction <- predict(model, boston_train)
boston_train_predictand <- boston_train[,"medv"]
train_eval <- evaluate(model, boston_train_predictand, train_prediction)
print(train_eval$metrics)
```

# Test
Test evaluation.

```{r}
test_prediction <- predict(model, boston_test)
boston_test_predictand <- boston_test[,"medv"]
test_eval <- evaluate(model, boston_test_predictand, test_prediction)
print(test_eval$metrics)
```

References
- Breiman, L. (2001). Random Forests. Machine Learning 45(1):5–32.
- Liaw, A. and Wiener, M. (2002). Classification and Regression by randomForest. R News.
