## Tutorial 04 - Preprocessing Basics

After the initial cleaning stage, the next question is how to make the attributes more suitable for modeling. Two common operations are scaling numeric variables and reducing redundancy among predictors.

This tutorial introduces both ideas in a compact way: normalization changes the scale, while correlation-based selection simplifies the feature set.

```{r}
# install.packages("daltoolbox")

library(daltoolbox)
```

Begin by inspecting the original scale of the `iris` attributes. Notice that each numeric column has a different range.
```{r}
iris <- datasets::iris
summary(iris)
```

Apply min-max normalization so that all numeric attributes are placed on a comparable scale. This is especially important for methods that are sensitive to distances or magnitudes.
```{r}
norm <- minmax()
norm <- fit(norm, iris)
iris_norm <- transform(norm, iris)

summary(iris_norm)
```

Once the variables are normalized, check whether some attributes are strongly redundant. Correlation-based feature selection can help simplify the dataset without manually inspecting each pair of variables.
```{r}
fs <- feature_selection_corr(cutoff = 0.9)
fs <- fit(fs, iris_norm)
```

Transform the dataset and compare the set of columns before and after selection. This shows the practical effect of the preprocessing step.
```{r}
iris_fs <- transform(fs, iris_norm)

names(iris_norm)
names(iris_fs)
head(iris_fs)
```

A beginner-friendly interpretation is: normalization prepares the scale, and feature selection prepares the structure of the data.
