## Tutorial 05 - Baseline Classification

A baseline is one of the healthiest habits in experimental work. Before testing advanced learners, it is useful to establish a simple reference that answers a basic question: is the stronger model actually adding value?

This tutorial compares a naive baseline with a more expressive but still interpretable classifier.

```{r}
# install.packages("daltoolbox")

library(daltoolbox)
```

Prepare the problem once so both learners face exactly the same data.
```{r}
iris <- datasets::iris
slevels <- levels(iris$Species)

set.seed(1)
sr <- train_test(sample_stratified("Species"), iris)
iris_train <- sr$train
iris_test <- sr$test
```

Train the majority classifier. It always predicts the most frequent class seen during training, so it is intentionally weak but very informative as a minimum benchmark.
```{r}
baseline <- cla_majority("Species", slevels)
baseline <- fit(baseline, iris_train)

baseline_pred <- predict(baseline, iris_test)
baseline_eval <- evaluate(baseline, adjust_class_label(iris_test$Species), baseline_pred)
baseline_eval$metrics
```

Now train a decision tree on the same split. Because the experimental conditions are unchanged, any improvement is easier to interpret.
```{r}
tree <- cla_dtree("Species", slevels)
tree <- fit(tree, iris_train)

tree_pred <- predict(tree, iris_test)
tree_eval <- evaluate(tree, adjust_class_label(iris_test$Species), tree_pred)
tree_eval$metrics
```

The practical lesson is simple: always compare a more elaborate model with a transparent baseline, not only with other elaborate models.
