## Tutorial 07 - Model Comparison

Once the baseline and the evaluation logic are clear, the next step is to compare multiple learners under the same conditions. The important idea is fairness: same dataset, same split, same metrics, different models.

This is where `daltoolbox` becomes useful as an experimental framework rather than just a collection of isolated functions.

```{r}
# install.packages("daltoolbox")

library(daltoolbox)
```

Prepare one shared train/test split. This keeps the comparison controlled.
```{r}
iris <- datasets::iris
slevels <- levels(iris$Species)

set.seed(1)
sr <- train_test(sample_stratified("Species"), iris)
iris_train <- sr$train
iris_test <- sr$test
```

Define a small group of learners. The set mixes a baseline, a local method, a tree, and an ensemble so the reader sees different model families.
```{r}
models <- list(
  majority = cla_majority("Species", slevels),
  tree = cla_dtree("Species", slevels),
  knn = cla_knn("Species", slevels, k = 5),
  rf = cla_rf("Species", slevels, mtry = 2, ntree = 10)
)
```

Fit and evaluate each learner using the same protocol.
```{r}
results <- lapply(models, function(model) {
  fitted <- fit(model, iris_train)
  pred <- predict(fitted, iris_test)
  evaluate(fitted, adjust_class_label(iris_test$Species), pred)$metrics
})

results
```

At this stage, the main pedagogical gain is methodological: the learner changes, but the experiment design stays stable.
