## Tutorial 10 - Regression Workflow

The Experiment Line idea is not limited to classification. In regression, the target becomes numeric, but the main stages remain the same: split, fit, predict, and evaluate.

This tutorial helps the learner see that the framework is stable even when the analytical task changes.

```{r}
# install.packages("daltoolbox")

library(daltoolbox)
library(MASS)
```

Load a numeric prediction problem. The goal is to predict `medv`, a continuous outcome.
```{r}
data(Boston)
head(Boston)

Boston <- as.matrix(Boston)
```

Create train and test partitions.
```{r}
set.seed(1)
sr <- sample_random()
sr <- train_test(sr, Boston)

boston_train <- sr$train
boston_test <- sr$test
```

Fit a regression tree and inspect both training and test errors.
```{r}
model <- reg_dtree("medv")
model <- fit(model, boston_train)

train_prediction <- predict(model, boston_train)
train_eval <- evaluate(model, boston_train[, "medv"], train_prediction)
train_eval$metrics

test_prediction <- predict(model, boston_test)
test_eval <- evaluate(model, boston_test[, "medv"], test_prediction)
test_eval$metrics
```

From a teaching perspective, this is a useful turning point: the workflow is familiar, but the interpretation of the metrics now belongs to regression rather than classification.
