## Tutorial 11 - Clustering Workflow

Clustering changes the analytical setting because there is no explicit target to predict during training. Even so, the workflow is still structured: choose a method, fit it, obtain cluster assignments, and inspect the result.

This tutorial also reinforces a recurring lesson from data mining: preprocessing can change unsupervised results substantially.

```{r}
# install.packages("daltoolbox")

library(daltoolbox)
```

Use only the numeric attributes of `iris` for clustering.
```{r}
iris <- datasets::iris
x <- iris[, 1:4]
```

Run K-means on the original scale.
```{r}
model <- cluster_kmeans(k = 3)
model <- fit(model, x)
clu <- cluster(model, x)

table(clu)
evaluate(model, clu, iris$Species)
```

Now normalize the data and repeat the same clustering procedure. Because the method is unchanged, any difference is due mainly to the representation of the data.
```{r}
norm <- fit(minmax(), iris)
iris_norm <- transform(norm, iris)
x_norm <- iris_norm[, 1:4]

model_norm <- cluster_kmeans(k = 3)
model_norm <- fit(model_norm, x_norm)
clu_norm <- cluster(model_norm, x_norm)

table(clu_norm)
evaluate(model_norm, clu_norm, iris$Species)
```

This is an important lesson for beginners: in unsupervised learning, the data representation can matter as much as the algorithm.
