## Tutorial 12 - Visual Analysis and Reporting

A mining workflow should not end with a metric table. Visual inspection helps the analyst understand the data, spot separation or overlap among groups, and communicate the result in a clearer way.

This tutorial uses one exploratory plot and one compact reporting table as a bridge between analysis and communication.

```{r}
# install.packages(c("daltoolbox", "ggplot2", "RColorBrewer", "dplyr"))

library(daltoolbox)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
```

Prepare a color palette and a shared theme so the plot is easier to read.
```{r}
colors <- brewer.pal(4, "Set1")
font <- theme(text = element_text(size = 16))

iris <- datasets::iris
```

Create a scatter plot to inspect how two numeric attributes relate to the class structure. This kind of chart is often useful before choosing a classifier.
```{r}
gr <- plot_scatter(
  iris |>
    dplyr::select(x = Sepal.Length, value = Sepal.Width, variable = Species),
  label_x = "Sepal.Length",
  label_y = "Sepal.Width",
  colors = colors[1:3]
) + font

plot(gr)
```

Now create a small comparison table that could appear in a report. The exact numbers are less important than the idea of communicating results in a compact and reproducible way.
```{r}
set.seed(1)
sr <- train_test(sample_stratified("Species"), iris)
slevels <- levels(iris$Species)

models <- list(
  majority = cla_majority("Species", slevels),
  tree = cla_dtree("Species", slevels)
)

report <- lapply(names(models), function(name) {
  fitted <- fit(models[[name]], sr$train)
  pred <- predict(fitted, sr$test)
  metrics <- evaluate(fitted, adjust_class_label(sr$test$Species), pred)$metrics
  data.frame(model = name, t(metrics), check.names = FALSE)
})

do.call(rbind, report)
```

For teaching purposes, this tutorial shows that analysis and communication should be treated as part of the same workflow.
