## Tutorial 22 - Clustering Workflow

Clustering changes the analytical setting because there is no explicit target to predict during training. Even so, the workflow is still structured: choose a method, fit it, obtain cluster assignments, and inspect the result.

This tutorial also reinforces a recurring lesson from data mining: preprocessing can change unsupervised results substantially.

```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# install.packages("daltoolbox")

library(daltoolbox)
```

Use only the numeric attributes of `iris` for clustering.
```{r}
iris <- datasets::iris
x <- iris[, 1:4]
```

Run K-means on the original scale.
```{r}
model <- cluster_kmeans(k = 3)
set_example_seed()
model <- daltoolbox::fit(model, x)
clu <- daltoolbox::cluster(model, x)

table(clu)
daltoolbox::evaluate(model, clu, iris$Species)
```

Now normalize the data and repeat the same clustering procedure. Because the method is unchanged, any difference is due mainly to the representation of the data.
```{r}
set_example_seed()
norm <- daltoolbox::fit(minmax(), iris)
iris_norm <- daltoolbox::transform(norm, iris)
x_norm <- iris_norm[, 1:4]

model_norm <- cluster_kmeans(k = 3)
set_example_seed()
model_norm <- daltoolbox::fit(model_norm, x_norm)
clu_norm <- daltoolbox::cluster(model_norm, x_norm)

table(clu_norm)
daltoolbox::evaluate(model_norm, clu_norm, iris$Species)
```

This is an important lesson for beginners: in unsupervised learning, the data representation can matter as much as the algorithm.

The evaluation used above is the default evaluation of `cluster_kmeans()`. These metric lists can be customized, but that is optional and is better treated as a separate modeling choice.
