About the chart
- Radar: displays multiple numeric variables on radial axes from a common origin; useful for comparative profiles.

Graphics environment setup.
```{r}
source(url("https://raw.githubusercontent.com/cefet-rj-dal/daltoolbox/main/examples/seed.R"))
# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

```{r}
library(ggplot2)
library(RColorBrewer)

# color palette
colors <- brewer.pal(4, 'Set1')

# setting the font size for all charts
font <- theme(text = element_text(size=16))
```

Mean per numeric variable and shaping the required format for radar.
```{r}
# iris dataset for the example
head(iris)
```

```{r}
library(dplyr)

data <- iris |> dplyr::select(-Species) 
data <- sapply(data, mean)
data <- data.frame(name = names(data), value = data) |> dplyr::arrange(name)

head(data)
```

```{r}

# Radar chart

# Graphical method to display multivariate data with 3+ quantitative variables on axes starting from the same point.

# More info: https://en.wikipedia.org/wiki/Radar_chart

grf <- plot_radar(data, colors=colors[1]) + font
plot(grf)
```

What to observe
- With four variables, the profile is a quadrilateral. In general, the radar profile is an n-sided polygon, where n is the number of variables.
- `plot_radar()` already sets the full drawing area, so adding `ylim()` can incorrectly cut the lower half of the figure.

References
- Wickham, H. (2016). ggplot2: Elegant Graphics for Data Analysis. Springer.
- Wilkinson, L. (2005). The Grammar of Graphics (2nd ed.). Springer.
