About the chart
- Histogram: distributes observations into bins along the x-axis; useful to visualize frequency and skewness.

Graphics environment setup.
```{r}
# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

```{r}
library(ggplot2)
library(RColorBrewer)

# color palette
colors <- brewer.pal(4, 'Set1')

# setting the font size for all charts
font <- theme(text = element_text(size=16))
```

Generate variables with distinct distributions (exponential, uniform, normal).
```{r}
# Examples with data distributions
# We use random variables to facilitate visualization of different distributions.

# example: dataset to be plotted  
example <- data.frame(exponential = rexp(100000, rate = 1), 
                     uniform = runif(100000, min = 2.5, max = 3.5), 
                     normal = rnorm(100000, mean=5))
head(example)
```

Histogram

Visualize the distribution of a continuous variable by binning the x-axis and counting observations per bin. `geom_histogram()` displays counts as bars.
More info: ?geom_histogram (R documentation)

Build histograms and arrange multiple charts side by side.
```{r}
library(dplyr)

grf <- plot_hist(example |> dplyr::select(exponential), 
                  label_x = "exponential", color=colors[1]) + font
options(repr.plot.width=5, repr.plot.height=4)
plot(grf)
```

Chart arrangement

Use `grid.arrange` to place the generated charts side by side.

```{r}
grfe <- plot_hist(example |> dplyr::select(exponential), 
                  label_x = "exponential", color=colors[1]) + font
grfu <- plot_hist(example |> dplyr::select(uniform), 
                  label_x = "uniform", color=colors[1]) + font  
grfn <- plot_hist(example |> dplyr::select(normal), 
                  label_x = "normal", color=colors[1]) + font 
```

```{r}
library(gridExtra)  

options(repr.plot.width=15, repr.plot.height=4)
grid.arrange(grfe, grfu, grfn, ncol=3)
```

References
- Freedman, D., and Diaconis, P. (1981). On the histogram as a density estimator: L2 theory. Zeitschrift für Wahrscheinlichkeitstheorie und verwandte Gebiete.
- Wickham, H. (2016). ggplot2: Elegant Graphics for Data Analysis. Springer.
