About the chart
- Scatter: assesses the relationship between two numeric variables, with optional coloring by group/category.

This example is worth reading slowly because it teaches two things at once: what analytical question a scatter plot answers and how the data must be shaped before plotting.

Didactic goal: learn to use the chart for reasoning about the data, not only for producing a figure.

Graphics environment setup and color palette.
```{r}
# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

```{r}
library(ggplot2)
library(RColorBrewer)

# color palette
colors <- brewer.pal(4, 'Set1')

# setting the font size for all charts
font <- theme(text = element_text(size=16))
```

Sample data (iris) for the chart.
```{r}
# iris dataset for the example
head(iris)
```

Build a scatter plot: select and rename columns to `x`, `value` (y), and `variable` (color).
```{r}
# Scatter plot

# Used to visualize the relationship between two numeric variables.
# The first selected column is treated as X (independent) and the second as Y (dependent);
# a third categorical variable can color the points.

# The color vector must match the number of levels/groups.

# More info: https://en.wikipedia.org/wiki/Scatter_plot

library(dplyr)

grf <- plot_scatter(
  iris |> dplyr::select(x = Sepal.Length, value = Sepal.Width, variable = Species),
  label_x = "Sepal.Length",  # X-axis label
  label_y = "Sepal.Width",   # Y-axis label
  colors=colors[1:3]          # one color per Species level
) + font
plot(grf)
```

What to observe
- The column names are adapted to the plotting helper, which is a useful reminder that visualization often starts with data organization.
- The species colors make it easier to see overlap and separation between groups.

Common mistakes
- Choosing two numeric variables without asking what relationship is being investigated.
- Using too many groups or colors, which makes the visual comparison harder.
- Treating the chart as final evidence instead of as part of exploratory analysis.

References
- Cleveland, W. S. (1994). The Elements of Graphing Data (2nd ed.). Hobart Press.
- Wickham, H. (2016). ggplot2: Elegant Graphics for Data Analysis. Springer.
