About the chart
- Time series (lines): points connected by segments; highlights trend and seasonality over time/ordered axis.

Graphics environment setup.
```{r}
# installation 
#install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

```{r}
library(ggplot2)
library(RColorBrewer)

# color palette
colors <- brewer.pal(4, 'Set1')

# setting the font size for all charts
font <- theme(text = element_text(size=16))
```

Synthetic series (sine and shifted cosine) for the example.
```{r}
# Synthetic time series

x <- seq(0, 10, 0.25)
serie <- data.frame(x, sin=sin(x), cosine=cos(x)+5)
head(serie)
```

Build a two-line series chart.
```{r}
# Series chart

# Displays a sequence of points connected by line segments. 

# Similar to scatter, but with an x-axis ordered by time/index.

# More info: https://en.wikipedia.org/wiki/Line_chart

grf <- plot_series(serie, colors=colors[1:2]) + font
plot(grf)
```

References
- Wickham, H. (2016). ggplot2: Elegant Graphics for Data Analysis. Springer.
- Hyndman, R. J., and Athanasopoulos, G. (2021). Forecasting: Principles and Practice (3rd ed.). OTexts.
