```{r}
# installation 
install.packages("daltoolbox")

# loading DAL
library(daltoolbox) 
```

```{r}
library(RColorBrewer)
# color palette
colors <- brewer.pal(4, 'Set1')

library(ggplot2)
# setting the font size for all charts
font <- theme(text = element_text(size=16))
```

# Examples using data distribution
The following examples use random variables so that different data distribution can be better viewed.

```{r}
# example4: dataset to be plotted  
example <- data.frame(exponential = rexp(100000, rate = 1), 
                     uniform = runif(100000, min = 2.5, max = 3.5), 
                     normal = rnorm(100000, mean=5))
head(example)
```

# Density plot

Computes and draws kernel density estimate, which is a smoothed version of the histogram. This is a useful alternative to the histogram for continuous data that comes from an underlying smooth distribution.

More information: ?geom_density (R documentation)

```{r}
options(repr.plot.width=8, repr.plot.height=5)
grf <- plot_density(example, colors=colors[1:3]) + font
plot(grf)
```

# Arrangement of graphs

Function $grid.arrange$ is used to position previously computed charts

```{r}
library(dplyr)
grfe <- plot_density(example |> dplyr::select(exponential), 
                     label_x = "exponential", color=colors[1]) + font  
grfu <- plot_density(example |> dplyr::select(uniform), 
                     label_x = "uniform", color=colors[2]) + font  
grfn <- plot_density(example |> dplyr::select(normal), 
                     label_x = "normal", color=colors[3]) + font 
```

```{r}
library(gridExtra)  
options(repr.plot.width=15, repr.plot.height=4)
grid.arrange(grfe, grfu, grfn, ncol=3)
```

